---
title: "Nutrient_Graphing"
author: "Sam Struthers"
format: html
editor: visual
---

# Set Up

This document is to work on graphs related to nutrients from Reservoirs/ Mainstem

```{r}
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")
#Determning number of Samples....

reservoir_chemistry <- read_feather("data/field_chemistry/cleaned/reservoir_chem_2021_2022_062023.feather")%>%
filter( watershed != "Comanche Reservoir" & watershed != "Hourglass Reservoir"& Year>= "2021")

meta_units_table <- read_csv("data/field_chemistry/Poudre_Portal_Data/Units_Cam_Peak.csv")



res_only_data <- reservoir_chemistry%>%
filter(location=="Reservoir")%>%
  pivot_longer(cols = c(ChlA, Turbidity, TSS, pH,ANC, Na, NH4, K, Mg, Ca, F, Cl, PO4, SO4, SC,NO3, DOC, DTN),names_to = "param", values_to = "value")





```

## Functions

```{r}

#timeline function

nutrient_timeline_graph <-  function(nutrient, title = FALSE){
  
  
  param_label <- filter(meta_units_table, Parameters == nutrient)%>%
    select(combined)%>%
    pull()
  


  if(title == FALSE){
         ## NO TITLE 
 notitle_graph <- res_only_data%>%
    filter(param == nutrient& !is.na(param))%>%
    ggplot(., aes(x=Date,y=value, color=Watershed_Level)) +
  geom_point(size=3) +
  geom_line(aes(group=site_code), size=1) +
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  #geom_abline(aes(slope=0, intercept=2.5), color='black', linetype="dashed") +
  labs(x = "", y = param_label) +
  theme_bw(base_size=28) +
  theme(legend.position = "none",
  strip.background = element_blank(),
  strip.text.x = element_blank())+
  facet_wrap(~Year, scales = "free_x")
 
 return(notitle_graph)
  }

## Title Plot
if(title == TRUE){
  title_graph <- res_only_data%>%
    filter(param == nutrient& !is.na(param))%>%
    ggplot(., aes(x=Date,y=value, color=Watershed_Level)) +
  geom_point( size=3) +
  geom_line(aes(group=site_code), size=1) +
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  #geom_abline(aes(slope=0, intercept=2.5), color='black', linetype="dashed") +
  labs(x = "", y = param_label) +
  theme_bw(base_size=28) +
  theme(legend.position = "none")+
  facet_wrap(~Year, scales = "free_x")
 
  return(title_graph)
}

  
}




#boxplot function

nutrient_boxplot_graph <-  function(nutrient, title = FALSE, graph_size = 28){
  
  
  param_label <- filter(meta_units_table, Parameters == nutrient)%>%
    select(combined)%>%
    pull()
  
         ## NO TITLE
  if(title == FALSE){
   
  no_title_graph <- res_only_data%>%
    filter(param == nutrient)%>%
  ggplot() +
  geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
  scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
                        guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=graph_size)+
  theme(legend.position = "none",
  strip.background = element_blank(),
  strip.text.x = element_blank())+
  labs(x = "", y = param_label)+
  facet_wrap(~Year)
  
 return( no_title_graph)
  }
  
  if(title == TRUE){
   
  title_graph <- res_only_data%>%
    filter(param == nutrient)%>%
  ggplot() +
  geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
  scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
                        guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=graph_size)+
  theme(legend.position = "none")+
  labs(x = "", y = param_label)+
  facet_wrap(~Year)
  
  return( title_graph)
  }
  
}





# nutrient_boxplot_swarm_graph = function(nutrient){
#   
#    param_label <- filter(meta_units_table, Parameters == nutrient)%>%
#     select(combined)%>%
#     pull()
#   
#   
#   res_only_data%>%
#     filter(param == nutrient)%>%
#   ggplot() +
#   geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
#     geom_quasirandom(aes(x=reorder(site_code,order,max),y=value, fill = Watershed_Level),colour = "black", cex = 2.5, alpha = .75)+
#   scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
#                         guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
#   theme_bw(base_size=28)+
#   theme(legend.position = "none",
#   strip.background = element_blank(),
#   strip.text.x = element_blank())+
#   labs(x = "", y = param_label)+
#   facet_wrap(~Year)
# }
# 
# nutrient_boxplot_swarm_graph_title = function(nutrient){
#   res_only_data%>%
#     filter( == nutrient)%>%
#   ggplot() +
#   geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
#      geom_quasirandom(aes(x=reorder(site_code,order,max),y=value),color = "black", cex = 2.5, alpha = .75)+
#   scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
#                         guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
#     scale_color_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
#                         guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
#   theme_bw(base_size=28)+
#   theme(legend.position = "none")+
#   labs(x = "", y = nutrient)+
#   facet_wrap(~Year)
# }

```

# Graphing

These are collected from grab samples at our reservoir sites. Samples are collected weekly between June and November and analyzed for key nutrients.

## Timeline 2021 and 2022 Reservoir data

```{r}

no3_timeline <-nutrient_timeline_graph( 'NO3')
po4_timeline <-nutrient_timeline_graph( 'PO4')
so4_timeline <-nutrient_timeline_graph( 'SO4')
chla_timeline <-nutrient_timeline_graph( 'ChlA')
pH_timeline <-nutrient_timeline_graph( 'pH')
tss_timeline <-nutrient_timeline_graph( 'TSS')
na_timeline <-nutrient_timeline_graph( 'Na', title = TRUE)
nh4_timeline <-nutrient_timeline_graph( 'NH4')
sc_timeline <-nutrient_timeline_graph( 'SC', title = TRUE)
k_timeline <-nutrient_timeline_graph( 'K')
mg_timeline <-nutrient_timeline_graph( 'Mg')
ca_timeline <-nutrient_timeline_graph( 'Ca')
f_timeline <-nutrient_timeline_graph( 'F')
cl_timeline <-nutrient_timeline_graph( 'Cl')



# timeline graphs 1

ggarrange(sc_timeline,no3_timeline,po4_timeline,so4_timeline,f_timeline,
          na_timeline, k_timeline,  ca_timeline, cl_timeline,mg_timeline,
          ncol=1, nrow=12)#, common.legend=T) 

ggarrange(sc_timeline,no3_timeline,po4_timeline,so4_timeline,f_timeline,
          ncol=1, nrow=5)
#ggsave('output/nutrient_timeline_1_final.jpg', width = 24, height = 20, units = "in", dpi = 300)

ggarrange(na_timeline, mg_timeline,k_timeline, ca_timeline, cl_timeline,   ncol=1, nrow=5)
#ggsave('output/nutrient_timeline_2_final.jpg', width = 24, height = 20, units = "in", dpi = 300)

# extra timeline graphs

ggarrange(na_timeline,mg_timeline,ca_timeline,f_timeline,cl_timeline, ncol=1, nrow=6)

#ggsave('output/extras_timeline_na_mg_ca_f_cl.jpg', width = 12.5, height = 16)


```

## Boxplots 2021 and 2022 Reservoir data

Mimics graphs from 2021 report. Faceted for 2022 data

```{r}

no3_boxplot <-nutrient_boxplot_graph( 'NO3', title = TRUE)
po4_boxplot <-nutrient_boxplot_graph( 'PO4')
so4_boxplot <-nutrient_boxplot_graph( 'SO4')
chla_boxplot <-nutrient_boxplot_graph( 'ChlA')
pH_boxplot <-nutrient_boxplot_graph( 'pH')
tss_boxplot <-nutrient_boxplot_graph( 'TSS')
na_boxplot <-nutrient_boxplot_graph( 'Na')
nh4_boxplot <-nutrient_boxplot_graph( 'NH4')
k_boxplot <-nutrient_boxplot_graph( 'K')
mg_boxplot <-nutrient_boxplot_graph( 'Mg')
ca_boxplot <-nutrient_boxplot_graph( 'Ca')
f_boxplot <-nutrient_boxplot_graph( 'F')
cl_boxplot <-nutrient_boxplot_graph( 'Cl')
sc_boxplot <- nutrient_boxplot_graph('SC', title = TRUE)


#boxplot fig 1

 ggarrange(sc_boxplot,no3_boxplot,po4_boxplot,so4_boxplot,k_boxplot,
           ncol=1, nrow=6)#, common.legend=T) 
 #ggsave('output/nutrient_boxplot_final_SC_NO3_PO4_SO4_K.jpg',
        width = 12.5, height = 16, dpi = 300)
 
 

#extra boxplot fig
ggarrange(no3_boxplot,po4_boxplot,k_boxplot, cl_boxplot, 
          ncol=1, nrow=4)
#ggsave('output/no3_po4_k_cl_boxplot_final.jpg',
       width = 12.5, height = 15, dpi = 300)


#Larger plot
ggarrange(no3_boxplot,po4_boxplot,so4_boxplot,k_boxplot,na_boxplot,
          sc_boxplot,mg_boxplot,ca_boxplot,f_boxplot,cl_boxplot,
          ncol=1, nrow=10)
#ggsave('output/nutrient_boxplot_final_ONEROW_SC_NO3_SO4_Mg_F_PO4_K_Na_Ca_Cl.jpg',
       width = 30, height = 36, units= "in",dpi = 300)


```

## 2022 Boxplots all sites

```{r}


all_sites_data <- reservoir_chemistry%>%
filter(site_code %in% mainstem_res_set)%>%
  pivot_longer(cols = c(ChlA, Turbidity, TSS, pH,ANC, Na, NH4, K, Mg, Ca, F, Cl, PO4, SO4, SC,NO3),names_to = "param", values_to = "value")






#boxplot function

nutrient_boxplot_all_sites <- function(nutrient, year_choice, title = FALSE){
  
  param_label <- filter(meta_units_table, Parameters == nutrient)%>%
    select(combined)%>%
    pull()
  
         ## NO TITLE
  if(title == FALSE){
   
  
  no_title_graph <- all_sites_data%>%
    filter(param == nutrient & Year ==  year_choice)%>%
  ggplot() +
  geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
  scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
                        guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=24)+
  theme(legend.position = "none",
  strip.background = element_blank(),
  strip.text.x = element_blank())+
  labs(x = "", y = param_label)
  return(no_title_graph)
  }
         ##  TITLE
  if(title == TRUE){
   
  
 title_graph <- all_sites_data%>%
    filter(param == nutrient & Year ==  year_choice)%>%
  ggplot() +
  geom_boxplot(aes(x=reorder(site_code,order,max),y=value, middle=mean(value), fill=Watershed_Level)) +
  scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", 
                        guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=24)+
   ggtitle(paste0(year_choice, " Data"))+
  theme(legend.position = "none",
        plot.title = element_text(family = '', face = 'bold', colour = 'black', size = 30, hjust = .5, vjust = .5))+
  labs(x = "", y = param_label)
 return(title_graph)
  }
  
}


## Using the function nutrient_boxplot_all_sites, create boxplots for following nutrients using year 2022 data: NO3, PO4, SO4, K, NH4, NA, SC, Mg, Ca, F, Cl
no3_2022_boxplot <- nutrient_boxplot_all_sites('NO3', '2022', title = TRUE)
po4_2022_boxplot <- nutrient_boxplot_all_sites('PO4', '2022')
so4_2022_boxplot <- nutrient_boxplot_all_sites('SO4', '2022')
k_2022_boxplot <- nutrient_boxplot_all_sites('K', '2022')
nh4_2022_boxplot <- nutrient_boxplot_all_sites('NH4', '2022')
na_2022_boxplot <- nutrient_boxplot_all_sites('Na', '2022')
sc_2022_boxplot <- nutrient_boxplot_all_sites('SC', '2022')
mg_2022_boxplot <- nutrient_boxplot_all_sites('Mg', '2022')
ca_2022_boxplot <- nutrient_boxplot_all_sites('Ca', '2022')
f_2022_boxplot <- nutrient_boxplot_all_sites('F', '2022')
cl_2022_boxplot <- nutrient_boxplot_all_sites('Cl', '2022')



ggarrange(no3_2022_boxplot,po4_2022_boxplot,so4_2022_boxplot,
          k_2022_boxplot,nh4_2022_boxplot,na_2022_boxplot,
          sc_2022_boxplot,mg_2022_boxplot,ca_2022_boxplot,
          f_2022_boxplot,cl_2022_boxplot,
          ncol=1, nrow=11)
#ggsave('output/nutrient_boxplot_2022_ONEROW_NO3_PO4_SO4_K_NH4_Na_SC_Mg_CA_F_Cl.jpg', width = 30, height = 36)


```

## 2021 Boxplots all sites

```{r}

## Using the function nutrient_boxplot_all_sites, create boxplots for following nutrients using year 2022 data: NO3, PO4, SO4, K, NH4, NA, SC, Mg, Ca, F, Cl
no3_2021_boxplot <- nutrient_boxplot_all_sites('NO3', '2021', title = TRUE)
po4_2021_boxplot <- nutrient_boxplot_all_sites('PO4', '2021')
so4_2021_boxplot <- nutrient_boxplot_all_sites('SO4', '2021')
k_2021_boxplot <- nutrient_boxplot_all_sites('K', '2021')
nh4_2021_boxplot <- nutrient_boxplot_all_sites('NH4', '2021')
na_2021_boxplot <- nutrient_boxplot_all_sites('Na', '2021')
sc_2021_boxplot <- nutrient_boxplot_all_sites('SC', '2021')
mg_2021_boxplot <- nutrient_boxplot_all_sites('Mg', '2021')
ca_2021_boxplot <- nutrient_boxplot_all_sites('Ca', '2021')
f_2021_boxplot <- nutrient_boxplot_all_sites('F', '2021')
cl_2021_boxplot <- nutrient_boxplot_all_sites('Cl', '2021')


plot(no3_2021_boxplot)

#arrange
ggarrange(no3_2021_boxplot,po4_2021_boxplot,so4_2021_boxplot,k_2021_boxplot,
          nh4_2021_boxplot,na_2021_boxplot,sc_2021_boxplot,mg_2021_boxplot,
          ca_2021_boxplot,f_2021_boxplot,cl_2021_boxplot,
          ncol=1, nrow=11)
#ggsave('output/nutrient_boxplot_2021_ONEROW_NO3_PO4_SO4_Mg_F_PO4_NH4_K_Na_Ca_Cl.jpg', width = 30, height = 36)
```

### 2021 vs 2022 comparison timelines Chambers Complex

```{r}


cbri_data <- filter(reservoir_chemistry, site_code %in% c( "CBRI")& Year >2020)%>%
  mutate(watershed = "Joe Wright Reservoir",
         location = "Outflow", 
         site_code = "JOEO")

comparison_plots_df <- filter(reservoir_chemistry, site_code %in% mainstem_res_set & Year >2020)%>%
  bind_rows(cbri_data)%>%
  filter( Date > "2021-05-30")%>%
  mutate(location = factor(location, levels = c("Inflow","Reservoir", "Outflow", "Stream", "Mainstem")), 
         watershed  = factor(watershed, levels = c("Long Draw Reservoir", 
                             "Joe Wright Reservoir", 
                             "Chambers Reservoir", 
                             "Peterson Reservoir", 
                             "Barnes Meadow Reservoir")))%>%
  pivot_longer(cols = c(ChlA, Turbidity, TSS, pH,ANC, Na, NH4, K, Mg, Ca, F, Cl, PO4, SO4, SC,NO3, DOC, DTN),names_to = "param", values_to = "value")

plot_comparison_timeline <- function(nutrient){

  param_label <- filter(meta_units_table, Parameters == nutrient)%>%
    select(combined)%>%
    pull()
  
  compare_df <- filter(comparison_plots_df, param == nutrient)%>%
    filter(!is.na(value))
  
comparison_plot <-  ggplot(compare_df)+
  geom_point(aes(x=Date, y = value, color=watershed, shape=watershed), size = 2.5)+
  geom_path(aes(x=Date, y = value, group=site_code, color = watershed), size = 1 )+
  #scale_fill_manual(values = colorsBS )+
  scale_color_manual(values = colorsBS)+
facet_wrap(~location + Year, scales = "free_x", ncol = 2, nrow = 3)+
theme_bw(base_size = 15)+
  theme(#legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
ylab(param_label)

return(comparison_plot)
}

nutrient_list<- select(meta_units_table, Parameters)%>%
    pull()


comparison_plots_list<- map(nutrient_list, plot_comparison_timeline)

for(i in 1:length(comparison_plots_list)){
  nutrient_list
  plot(comparison_plots_list[[i]])
  
}


```

# Trends across location

Are there any trends across location with respect to chla /nutrients?

-   NO3

-   Chl-A

-   PO4

-   SO4

-   K

#### DFs

```{r}
Reservoir_systems_Chemistry <- filter(reservoir_chemistry,
                                      site_code %in% All_res_system 
                                      & Year >= "2021" 
                                      & !is.na(ChlA))%>%
  mutate(location = factor(location, levels = c("Inflow","Reservoir", "Outflow")))


```

### Chl-A + SC + NO3

```{r}

##Chl-A grouped
In_Res_out_chla <- Reservoir_systems_Chemistry%>%
  ggplot(aes(x=reorder(site_code,order,max),y=ChlA, group= site_code, fill = Watershed_Level))+
  geom_boxplot(aes(x=reorder(site_code,order,max),y=ChlA, middle=mean(ChlA), fill= Watershed_Level))+
  geom_dotplot(stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .1, dotsize = 2)+
  scale_fill_gradient2(name="Watershed Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
  theme_bw(base_size = 10)+
   theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold"),
         strip.text.x = element_text(size = 12)) +
  coord_cartesian(ylim=c(0,12))+
  labs(x ="Site", y="Chl-A (mg/L)")+
  facet_wrap(~location, scales= "free_x") 

#plot(In_Res_out_chla)


#ggsave("output/CHLA_Grouped_Sites.jpg", width = 16, height = 9 )



##NO3


In_Res_out_NO3_Grouped <- Reservoir_systems_Chemistry%>%
  ggplot()+
  geom_boxplot(aes(x=reorder(location,order,max),y=NO3, middle=mean(NO3), fill= location))+
  geom_dotplot(aes(x=reorder(location,order,max),y= NO3, fill= location), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .04, dotsize = 1, alpha =.8)+
  scale_fill_manual(values = c("#56B4E9", "#F0E442", "#D55E00"))+
    theme_bw()+ 
   theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
  labs( x = "", y = "NO3 (mg/L)")
  

#plot(In_Res_out_NO3_Grouped)


#K
In_Res_out_K_Grouped <- Reservoir_systems_Chemistry%>%
  ggplot()+
  geom_boxplot(aes(x=reorder(location,order,max),y=K, middle=mean(K), fill= location))+
  geom_dotplot(aes(x=reorder(location,order,max),y= K, fill= location), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .1, dotsize = .25)+
  scale_fill_manual(values = c("#56B4E9", "#F0E442", "#D55E00"))+
    theme_bw()+ 
   theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
  labs( x = "", y = "K (mg/L)")

#plot(In_Res_out_K_Grouped)

#SO4
In_Res_out_SO4_Grouped <- Reservoir_systems_Chemistry%>%
  ggplot()+
  geom_boxplot(aes(x=reorder(location,order,max),y=SO4, middle=mean(SO4), fill= location))+
  geom_dotplot(aes(x=reorder(location,order,max),y= SO4, fill= location), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .2, dotsize = 2)+
  scale_fill_manual(values = c("#56B4E9", "#F0E442", "#D55E00"))+
    theme_bw()+ 
   theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
  labs( x = "Site Type", y = "SO4 (mg/L)")

#plot(In_Res_out_SO4_Grouped)

# NH4
In_Res_out_NH4_Grouped <- Reservoir_systems_Chemistry%>%
  ggplot()+
  geom_boxplot(aes(x=reorder(location,order,max),y=NH4, middle=mean(NH4), fill= location), alpha = 1)+
  geom_dotplot(aes(x=reorder(location,order,max),y= NH4, fill= location), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .005, dotsize = 2, alpha = .5)+
  scale_fill_manual(values = c("#56B4E9", "#F0E442", "#D55E00"))+
    theme_bw()+ 
   theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
  labs( x = "Site Type", y = "NH4 (mg/L)") 

#plot(In_Res_out_NH4_Grouped)


## Chl-A grouped by location


In_Res_out_chla_grouped <- Reservoir_systems_Chemistry%>%
  ggplot()+
  
  geom_boxplot(aes(x=reorder(location,order,max),y= ChlA, middle=mean(ChlA), fill= location))+
 # geom_violin(aes(x=reorder(location,order,max),y= ChlA, middle=mean(ChlA), fill= location),alpha = .5)+
  geom_dotplot(aes(x=reorder(location,order,max),y= ChlA, fill= location), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .1, dotsize = 2)+
  
  scale_fill_manual(values = c("#56B4E9", "#F0E442", "#D55E00"))+
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
  theme_bw()+ 
  theme(legend.position = "none", 
         axis.text=element_text(size=12),
         axis.title=element_text(size=14,face="bold")) +
  labs( x = "", y = "Chlorophyll a (μg/L)")+
  coord_cartesian(ylim=c(0,12))
  #facet_wrap(~Variable, scales= "free",nrow = 2, ncol = 6) 

plot(In_Res_out_chla_grouped)

#ggsave("output/location_Grouped_Chla_Boxplot.jpg", width = 11, height = 9)

# Plotting SO4, NO3, CHLA, K together

#ggarrange(In_Res_out_chla_grouped,In_Res_out_NO3_Grouped,In_Res_out_K_Grouped,In_Res_out_SO4_Grouped, In_Res_out_NH4_Grouped, ncol= 1, nrow = 5)---

```

## NO3/K ratio

```{r}


res_chem_k_no3 <- filter(reservoir_chemistry, site_code %in% mainstem_res_set & Year >2020)%>%
  filter(location == "Reservoir")%>%
  mutate(k_no3 = K/NO3,
         no3_k = NO3/K,
         site_year = paste(site_code, Year, sep = " "),
         Month =month.abb[month(Date)] ,
         day_of_year = yday(Date))

res_chem_k_no3$Month <- factor(res_chem_k_no3$Month, levels = c("Jun","Jul","Aug","Sep","Oct"))
#DdD




#ggarrange(no3_k, k_no3, ncol = 1, nrow = 2)

no3_vs_k <- res_chem_k_no3%>%
  ggplot()+
  geom_point(aes(x= K, y= NO3, color= Watershed_Level, size = Month), alpha = .5)+
  geom_smooth(aes(x= K, y= NO3), color = "black", method = "lm", se= F)+
  scale_size_manual(values = c(1,4,7,10,13))+
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=15) +
  theme(legend.position = "none") +
  labs( x = "K (mg/L)", y = "NO3 (mg/L) ")
#ggsave("test_fig/K_vs_no3.jpg", width = 11, height = 9)




k_vs_chla <- res_chem_k_no3%>%
  ggplot()+
  geom_point(aes(x= K, y= ChlA, color= Watershed_Level, size = Month), alpha = .5)+
  geom_smooth(aes(x= K, y= ChlA), color = "black", method = "lm", se= F)+
  scale_size_manual(values = c(1,4,7,10,13))+
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=15) +
 # theme(legend.position = "none") +
  labs( x = "K (mg/L)", y = "Chlorophyll a (μg/L)")

plot(k_vs_chla)
#ggsave("test_fig/K_vs_chla.jpg", width = 11, height = 9)


no3_vs_chla <- res_chem_k_no3%>%
  ggplot()+
  geom_point(aes(x= NO3, y= ChlA, color= Watershed_Level, size = Month), alpha = .5)+
  geom_smooth(aes(x= NO3, y= ChlA), color = "black", method = "lm", se= F)+
  scale_size_manual(values = c(1,4,7,10,13))+
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=15) +
 # theme(legend.position = "none") +
  labs( x = "NO3", y = "Chlorophyll a (μg/L)")

#plot(no3_vs_chla)


#ggsave("test_fig/NO3_vs_chla.jpg", width = 11, height = 9)

k_no3_vs_chla <- res_chem_k_no3%>%
  ggplot()+
  geom_point(aes(x= k_no3, y= ChlA, color= Watershed_Level))+
  scale_color_gradient2(name="Contributing Area Burn Intensity",low="#56B4E9", mid="#F0E442", high="#D55E00", guide="colourbar", midpoint=0.225, limits=c(0,0.45576),) +
  theme_bw(base_size=15) +
  theme(legend.position = "none") +
  labs( x = "K/NO3", y = "ChlA")
#plot(k_no3_vs_chla)

#ggsave("test_fig/k_no3_vs_chla.jpg", width = 11, height = 9)
```

## Means

```{r}

mean_nutrients <- reservoir_chemistry%>%
  select(c(ChlA, Turbidity, TSS, pH,ANC, Na, NH4, K, Mg, Ca, F, Cl, PO4, SO4, SC,NO3, site_code, Year))%>%
  na.omit()%>%
  group_by(site_code, Year)%>%
  summarise(mean_chla = mean(ChlA), 
            mean_turb = mean(Turbidity),
            mean_pH = mean(pH),
            mean_na = mean(Na),
            mean_nh4 = mean(NH4),
            mean_k = mean(K),
            mean_mg = mean(Mg),
            mean_ca = mean(Ca),
            mean_f = mean(F),
            mean_cl = mean(Cl),
            mean_po4 = mean(PO4),
            mean_so4 = mean(SO4),
            mean_sc = mean(SC),
            mean_no3 = mean(NO3))

write.csv(mean_nutrients, "data/mean_nutrients_2021_2022.csv")
```

## Conclusions!

This is the end of the document.
