---
title: "ROSS lab Reservoir Study Data Sharing"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
library(downloadthis)
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")

```

```{r}
#| eval: false
#| echo: false
#| message: false

download_dir(
  path = paste0(getwd(), "/sharing_data/field_chemistry/cleaned/"),
  output_name = "course-data",
  button_label = "Download Data",
  button_type = "success",
  icon = "fa fa-save",
  self_contained = FALSE
)

```

# Data

## Data Available

The data available at this site is grab sample chemistry data collected and processed at the RMRS Biogeochemistry lab. The data available here has been QA/QC'd and should be treated as final data.

## Download data

::: {.callout-note appearance="minimal"}
<i class="bi bi-download"></i> [Download CPF_reservoir_chemistry_up_to_110122 dataset](sharing_data/field_chemistry/cleaned/CPF_reservoir_chemistry_up_to_110122.csv){download="CPF_reservoir_chemistry_up_to_110122.csv"}
:::

::: {.callout-note appearance="minimal"}
<i class="bi bi-download"></i> [Download mean nutrients dataset](sharing_data/field_chemistry/cleaned/mean_nutrients_2021_2022.csv){download="CPF_Res_mean_nutrient_data.csv"}
:::

# Plots

## Plot 1: Longitudinal view of Joe Wright Creek

```{r}

```

## Plot 2: Longitudinal view of Joe Wright Creek and the Mainstem CLP
