---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("src/00_analysis_setup.R")
```

# Grab data

```{r}
#discrete sample data and location metadata from most recent pub
data_version = "v10.18.23"
source("src/analysis_fxns/grab_zenodo_data.R")

all_params <- chem_units%>%
  pull(simple)
# sensor data
source("src/analysis_fxns/grab_sensor_data.R")

```

## Date/Times not in Zenodo dataset

This will be incorporated into the next data release, until then this is how this data will be added

```{r}
time_data <- read_csv_arrow("data/field_chemistry/raw//sites_times_data_20231117.csv")%>%
  mutate(Date = as.Date(Date, format = "%d-%b-%y"), 
         Year = year(Date))%>%
  filter(Era == "FCW" & Year >= 2020)%>%
  select(FCW_Number = EraSamp , Time, Field_DO_mgL, `Field_Cond_µS/cm`, Field_Temp_C)
```

## Tidy discrete

```{r}
tidy_chem <- most_recent_chem%>%
  filter(Year > 2020)%>%
  left_join(time_data, by = "FCW_Number")%>%
  mutate(dt = case_when( !is.na(Time) ~ as.POSIXct(paste0(Date," ", Time), format = "%Y-%m-%d %H:%M"), 
                         TRUE ~ NA), 
         distance_upstream_km = case_when(site_code == "PFAL" ~ 73.9, TRUE ~ distance_upstream_km))%>%
  left_join(order_table, by = "site_code") 
#time data and site order now added to tidy chem and thus not needed
rm(time_data, order_table)

```
## Run above to get data loaded

```{r}
print("Data Successfully loaded for analysis")
```
# Map

Things in map
WQ sensor sites
JWC+BS res
Beav Sites
Mainstem

 Things to include in the site
- what part of the study
_ # of samples per year
- if sensor, POR for sensor deployment and # of match ups between sonde and grab
- if reservoir, # of RS match ups

## Create data frames

### All sites samples

```{r}


sample_nums <- most_recent_chem %>%
  # mutate(site_code = case_when(
  #   site_code == "SLEP" ~"PFAL", 
  #   TRUE ~ site_code
  # ))%>%
  group_by(site_code, Year) %>%
  count(name = "samples") %>%
  pivot_wider(names_from = Year, values_from = samples, values_fill = 0)%>%
  mutate(`# of samples (2021 & 2022)` = `2021` +`2022`)%>%
  select(site_code, `# of samples (2023)` = `2023`, `# of samples (2021 & 2022)`)
  




```


### sensors
```{r}
PBR <- tibble(site_code = "PBR",
  POR = "2023-4-20 : 2023-11-13",
              sensor_measurements = 13364,
              unique_parameters = "pH, Turbidity, Specific Conductivity, DO, Temperature")

sensor_sites <- sensor_data %>%
  filter(parameter %nin% c("% Saturation O₂","Resistivity", "ORP", "Actual Conductivity" ))%>%
  group_by(site)%>%
  dplyr::summarise(min_date = as.Date(min(timestamp)),
                   max_date = as.Date(max(timestamp)), 
                   sensor_measurements = n_distinct(timestamp),
    unique_parameters = toString(unique(parameter)) 
                   )%>%
  ungroup()%>%
  mutate(POR = paste0(min_date, " : ", max_date),
         site_code = toupper(site))%>%
  plyr::rbind.fill(PBR)%>%
  left_join(most_recent_meta, by = "site_code")%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%
  select(Site_Name, POR,sensor_measurements, unique_parameters,watershed, `# of samples (2023)`, `# of samples (2021 & 2022)`)
  

mapview::mapview(sensor_sites, layer.name = "Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)

```

### reservoirs

```{r}


CLP_RS <- read_feather("data/RS/CLP_point_DSWE1_for_analysis_2023-12-08.feather")%>%
  filter(year(date)%in% c(2021, 2022, 2023)& GNIS_Name %in% c("Chambers Lake", "Comanche Reservoir",
                                                              "Barnes Meadow Reservoir",
                                                              "Joe Wright Reservoir", "Long Draw Reservoir", 
                                                              "Hourglass Reservoir", "Peterson Lake" ))%>%
  select(site_name = GNIS_Name, date)%>%
  mutate(site_code = case_when(
    site_name == "Chambers Lake" ~ "CBRR", 
    site_name == "Barnes Meadow Reservoir" ~ "BRNR", 
    site_name == "Joe Wright Reservoir" ~ "JOER", 
    site_name == "Long Draw Reservoir" ~ "LNGR", 
    site_name == "Peterson Lake" ~ "PTRR", 
    site_name == "Comanche Reservoir" ~ "COMR", 
    site_name == "Hourglass Reservoir" ~ "HORR"))%>%
  rename(RS_date = date)%>%
  distinct()


# for each RS image, see if there is a grab sample at the same site and the grab date is within +-3 days of RS image

RS_match_ups <- tibble()
for(i in 1:nrow(CLP_RS)){
  rs_loop <- most_recent_chem%>%
    filter(site_code == CLP_RS$site_code[i] & Date >= (CLP_RS$RS_date[i] - days(4)) & Date <= (CLP_RS$RS_date[i] + days(4)))%>%
    mutate(RS_date = CLP_RS$RS_date[i])%>%
    rename(grab_date = Date)
  
  RS_match_ups <- rbind(RS_match_ups, rs_loop)
  rm(rs_loop, i)
}



RS_matches_summary <- RS_match_ups%>%
  group_by(site_code, Year)%>%
  summarise(`Grab and RS Matches (within 4 days)` = n())

images_overall <- CLP_RS%>%
  filter(month(RS_date)>=5 & month(RS_date)<=11)%>%
  mutate(Year = year(RS_date))%>%
  group_by(Year, site_code)%>%
  summarise(`RS Images` = n())%>%
  left_join(RS_matches_summary, by = c("Year", "site_code"))

images_2021_2022 <- filter(images_overall, Year %in% c(2021, 2022))%>%
  group_by(site_code)%>%
  summarise(`RS Images (2021 and 2022)` = sum(`RS Images`), 
            `Grab and RS Matches (2021 and 2022)` = sum(`Grab and RS Matches (within 4 days)`))

reservoir_sites <- filter(images_overall, Year == 2023)%>%
  left_join(images_2021_2022, by = "site_code")%>%
  left_join(most_recent_meta, by = "site_code")%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%

  select(Site_Name, `2023 Grab and RS Matches (within 4 days)` = `Grab and RS Matches (within 4 days)`,
         `2023 RS Images` = `RS Images`,`RS Images (2021 and 2022)`, `# of samples (2023)`, `Grab and RS Matches (2021 and 2022)`, `# of samples (2021 & 2022)`)

mapview::mapview(reservoir_sites, layer.name = "Reservoir Sites",col.regions = "#009E73", cex = 8)+
mapview::mapview(sensor_sites, layer.name = "Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)


```

### Additional Grab locations
all the sites we sample with no sensor and no RS

```{r}
  add_sampling <- filter(most_recent_meta, Campaign %in% c("Mainstem","South Fork","Chambers Complex","Longdraw" )& site_code %nin% unique(CLP_RS$site_code) & site_code %nin% c("JOEI", "CBRI", "PBR",  "CHD","LRT",  "SFM", "PBD", "SLEP")& watershed != "CLP  Mainstem-Fort Collins" )%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%
  select(Site_Name, `# of samples (2023)`, `# of samples (2021 & 2022)`, watershed)

Manners_bridge <- tibble(Site_Name = "Manner's Bridge WQ",
  POR = "2023-3-23 : 2023-11-13",
              sensor_measurements = 28712,
              unique_parameters = "pH, Turbidity, Specific Conductivity, DO, Temperature", 
              Long = -105.268816, 
              Lat = 40.696629   )%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)

mapview::mapview(reservoir_sites, layer.name = "Sampled Reservoir Sites",col.regions = "#009E73", cex = 8)+
mapview::mapview(sensor_sites, layer.name = "Sampled Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)+ 
  mapview::mapview(add_sampling, layer.name = "Additional Water Sampling",col.regions = "#D55E00", cex = 4)+
  mapview::mapview(Manners_bridge, layer.name = "Manner's Bridge WQ: FC Monitoring", col.regions = "#CC79A7", cex= 6 )


```



