---
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("src/00_analysis_setup.R")
```

# Grab data

```{r}
#discrete sample data and location metadata from most recent pub
DOI = "10372690"
data_version = "v12.13.23b"
source("src/analysis_fxns/grab_zenodo_data.R")

all_params <- chem_units%>%
  pull(simple)
# sensor data
source("src/analysis_fxns/grab_sensor_data.R")

```


## Tidy discrete

```{r}
tidy_chem <- most_recent_chem%>%
  filter(Year > 2020)%>%
  mutate(distance_upstream_km = case_when(site_code == "PFAL" ~ 73.9, TRUE ~ distance_upstream_km))%>%
  left_join(order_table, by = "site_code") 
#site order now added to tidy chem and thus not needed
rm(order_table)

```
## Run above to get data loaded

```{r}
print("Data Successfully loaded for analysis")
```

# Map

Things in map
WQ sensor sites
JWC+BS res
Beav Sites
Mainstem

 Things to include in the site
- what part of the study
_ # of samples per year
- if sensor, POR for sensor deployment and # of match ups between sonde and grab
- if reservoir, # of RS match ups

## Create data frames

### All sites samples

```{r}


sample_nums <- tidy_chem %>%
  # mutate(site_code = case_when(
  #   site_code == "SLEP" ~"PFAL", 
  #   TRUE ~ site_code
  # ))%>%
  group_by(site_code, Year) %>%
  count(name = "samples") %>%
  pivot_wider(names_from = Year, values_from = samples, values_fill = 0)%>%
  mutate(`# of samples (2021 & 2022)` = `2021` +`2022`)%>%
  select(site_code, `# of samples (2023)` = `2023`, `# of samples (2021 & 2022)`)
  




```


### sensors
```{r}
PBR <- tibble(site_code = "PBR",
              min_date = as.Date("2023-4-20"), 
              max_date = as.Date("2023-11-13"),
  POR = "2023-4-20 : 2023-11-13",
              sensor_measurements = 13364,
              unique_parameters = "pH, Turbidity, Specific Conductivity, DO, Temperature")

sensor_POR <- sensor_data %>%
  filter(parameter %nin% c("% Saturation O₂","Resistivity", "ORP", "Actual Conductivity" ))%>%
  group_by(site)%>%
  dplyr::summarise(min_date = as.Date(min(timestamp)),
                   max_date = as.Date(max(timestamp)), 
                   sensor_measurements = n_distinct(timestamp),
    unique_parameters = toString(unique(parameter)) 
                   )%>%
  ungroup()%>%
  mutate(POR = paste0(min_date, " : ", max_date),
         site_code = toupper(site))%>%
  plyr::rbind.fill(PBR)

matching_counts <- tidy_chem %>%
  inner_join(sensor_POR, by = "site_code") %>%
  filter(between(x = Date,  left = min_date, right = max_date)) %>%
  group_by(site_code) %>%
  count(name = "Sensor and Grab Matches (2023)")


sensor_sites <- sensor_POR%>%
  left_join(matching_counts, by = "site_code")%>%
  left_join(most_recent_meta, by = "site_code")%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%
  select(Site_Name, POR, `# of samples (2023)`,`Sensor and Grab Matches (2023)`,sensor_measurements, unique_parameters,watershed, `# of samples (2021 & 2022)`)
  

mapview::mapview(sensor_sites, layer.name = "Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)

```

### reservoirs

```{r}


CLP_RS <- read_feather("data/RS/CLP_point_DSWE1_for_analysis_2023-12-08.feather")%>%
  filter(year(date)%in% c(2021, 2022, 2023)& GNIS_Name %in% c("Chambers Lake", "Comanche Reservoir",
                                                              "Barnes Meadow Reservoir",
                                                              "Joe Wright Reservoir", "Long Draw Reservoir", 
                                                              "Hourglass Reservoir", "Peterson Lake" ))%>%
  select(site_name = GNIS_Name, date)%>%
  mutate(site_code = case_when(
    site_name == "Chambers Lake" ~ "CBRR", 
    site_name == "Barnes Meadow Reservoir" ~ "BRNR", 
    site_name == "Joe Wright Reservoir" ~ "JOER", 
    site_name == "Long Draw Reservoir" ~ "LNGR", 
    site_name == "Peterson Lake" ~ "PTRR", 
    site_name == "Comanche Reservoir" ~ "COMR", 
    site_name == "Hourglass Reservoir" ~ "HORR"))%>%
  rename(RS_date = date)%>%
  distinct()


# for each RS image, see if there is a grab sample at the same site and the grab date is within +-3 days of RS image

RS_match_ups <- tibble()
for(i in 1:nrow(CLP_RS)){
  rs_loop <- tidy_chem%>%
    filter(site_code == CLP_RS$site_code[i] & Date >= (CLP_RS$RS_date[i] - days(4)) & Date <= (CLP_RS$RS_date[i] + days(4)))%>%
    mutate(RS_date = CLP_RS$RS_date[i])%>%
    rename(grab_date = Date)
  
  RS_match_ups <- rbind(RS_match_ups, rs_loop)
  rm(rs_loop, i)
}



RS_matches_summary <- RS_match_ups%>%
  group_by(site_code, Year)%>%
  summarise(`Grab and RS Matches (within 4 days)` = n())

images_overall <- CLP_RS%>%
  filter(month(RS_date)>=5 & month(RS_date)<=11)%>%
  mutate(Year = year(RS_date))%>%
  group_by(Year, site_code)%>%
  summarise(`RS Images` = n())%>%
  left_join(RS_matches_summary, by = c("Year", "site_code"))

images_2021_2022 <- filter(images_overall, Year %in% c(2021, 2022))%>%
  group_by(site_code)%>%
  summarise(`RS Images (2021 and 2022)` = sum(`RS Images`), 
            `Grab and RS Matches (2021 and 2022)` = sum(`Grab and RS Matches (within 4 days)`))

reservoir_sites <- filter(images_overall, Year == 2023)%>%
  left_join(images_2021_2022, by = "site_code")%>%
  left_join(most_recent_meta, by = "site_code")%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%

  select(Site_Name, `2023 Grab and RS Matches (within 4 days)` = `Grab and RS Matches (within 4 days)`,
         `2023 RS Images` = `RS Images`, `# of samples (2023)`, `Grab and RS Matches (2021 and 2022)`,`RS Images (2021 and 2022)`, `# of samples (2021 & 2022)`)

mapview::mapview(reservoir_sites, layer.name = "Reservoir Sites",col.regions = "#009E73", cex = 8)+
mapview::mapview(sensor_sites, layer.name = "Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)


```

### Additional Grab locations
all the sites we sample with no sensor and no RS

```{r}
  add_sampling <- filter(tidy_chem, Campaign %in% c("Mainstem","South Fork","Chambers Complex","Longdraw" )& site_code %nin% unique(CLP_RS$site_code) & site_code %nin% c("JOEI", "CBRI", "PBR",  "CHD","LRT",  "SFM", "PBD", "SLEP")& watershed != "CLP  Mainstem-Fort Collins" )%>%
  left_join(sample_nums, by = "site_code")%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)%>%
  select(Site, `# of samples (2023)`, `# of samples (2021 & 2022)`, watershed)

Manners_bridge <- tibble(Site_Name = "Manner's Bridge WQ",
  POR = "2023-3-23 : 2023-11-13",
              sensor_measurements = 28712,
              unique_parameters = "pH, Turbidity, Specific Conductivity, DO, Temperature", 
              Long = -105.268816, 
              Lat = 40.696629   )%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)

mapview::mapview(reservoir_sites, layer.name = "Sampled Reservoir Sites",col.regions = "#009E73", cex = 8)+
mapview::mapview(sensor_sites, layer.name = "Sampled Water Quality Sensor Sites",col.regions = "#34b1eb", cex = 8)+ 
  mapview::mapview(add_sampling, layer.name = "Additional Water Sampling",col.regions = "#D55E00", cex = 4)+
  mapview::mapview(Manners_bridge, layer.name = "Manner's Bridge WQ: FC Monitoring", col.regions = "#CC79A7", cex= 6 )


```


# Map for funder report

```{r}
sites <- most_recent_meta%>%
  select(site_code, Lat, Long)%>%
  filter(site_code %in% c(
    #Reservoirs
    "JOEI", "JOER", "CBRI",  "CBRR", "CHD", "BRNR", "PTRR", "LNGR", "COMR", "HORR",
    #Mainstem
      "JWC", "PJW", "PFAL", "PBR", "SFM", "PSF", "PNF", "PBD",
    # Trib
    "NJOE", "ROAR", "LRT", "SHEP", "BLAK", "FISH", "BEAV", "BENN", "PENN")
  )%>%
  mutate( map_2021_2022  = case_when(
    site_code %in% c("JOEI", "JOER", "CBRI",  "CBRR", "CHD", "BRNR", "PTRR", "LNGR") ~ "weekly", 
    site_code %in% c("JWC", "PJW", "PFAL", "PBR", "SFM", "PSF", "PNF", "PBD") ~ "bi-weekly", 
    site_code %in% c("COMR", "HORR") ~ "monthly", 
    site_code %in% c("NJOE", "ROAR", "LRT", "SHEP", "BLAK", "FISH", "BEAV", "BENN", "PENN") ~ "trib"
  ), 
   map_2023  = case_when(
    site_code %in% c( "JOER",   "BRNR", "PTRR", "LNGR", "JWC", "PJW", "PBR", "PSF", "PNF", "COMR", "HORR", "BEAV") ~ "bi and monthly", 
    site_code %in% c("JOEI", "CBRI", "CHD","PFAL", "SFM", "PBD" ) ~ "sensor",
    site_code %in% c("NJOE", "ROAR", "LRT", "SHEP", "BLAK", "FISH", "BENN", "PENN") ~ "trib"
  ))%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)

map <- mapview::mapview(filter(sites, map_2021_2022 == "trib"), layer.name = "trib",col.regions = "#999999", cex = 6, alpha =1)+ mapview::mapview(filter(sites, map_2021_2022 == "weekly"), layer.name =  "weekly",col.regions = "#ff0303", cex = 10, alpha = 1 )+
       mapview::mapview(filter(sites, map_2021_2022 == "bi-weekly" ), layer.name = "biweek",col.regions = "#03ffff", cex = 10,alpha = 1)+
       mapview::mapview(filter(sites, map_2021_2022 == "monthly"), layer.name = "comr",col.regions = "#184dff", cex = 10,alpha = 1)
       
map


map <- mapview::mapview(filter(sites, map_2023 == "trib"), layer.name = "trib",col.regions = "#999999", cex = 5, alpha =1)+
  mapview::mapview(filter(sites, map_2023 == "bi and monthly" ), layer.name = "biweek",col.regions = "#BE398D", cex = 6,alpha = 1)+ mapview::mapview(filter(sites, map_2023 == "sensor"), layer.name =  "weekly",col.regions = "#000000", cex = 6, alpha = 1 )
       
       
map

```










