---
title: "larimer_q_downloader"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
source("package_loader.R")
```

# Sites with Q

This section will create urls for used to pull in all sites in the  Cache La Poudre (CLP) and Big Thompson (BIGT) watersheds. 

## Functions

```{r url functions}
#Create urls for metadata pulls
create_meta_url <- function(site_num){

  start_url <- "https://larimerco-ns5.trilynx-novastar.systems/novastar/data/api/v1/stationSummaries?forOperatorStationDashboard=true&stationNumId="
  final_url <- tibble( site_number = site_num, 
                       site_url = paste0(start_url, site_num))
  return(final_url)
}

#Create urls for Q or other sensor pulling
create_data_url <- function(site_num){
  end_dt <- "2023-01-24T13:30:00-07:00"
  start_url <- "https://larimerco-ns5.trilynx-novastar.systems/novastar/data/api/v1/stationSummaries?forOperatorStationDashboard=true&stationNumId="
  mid_url <- "&periodStart=2021-01-01T00:00:00-07:00&periodEnd="
  
  final_url <- tibble( site_number = site_num, 
                      site_url = paste0(start_url, site_num, mid_url, end_dt))
  return(final_url)
}

```

## Create urls
```{r}
#Station numbers
clp_Q_site_nums <- tibble(station_ids = c("11531", "11530", "11525", 
                    "11514", "11004", "11515",
                    "11518", "11517", "11516",
                    "6770", "11083", "11082",
                    "11009","7130","10408", "11021"))
bigt_Q_site_nums <- tibble(station_ids = c("11567","11566","11564",
                                           "11563","11562","11561",
                                           "11560", "11559","11558",
                                          "95100", "95000","3640",
                                          "3610","3570","3520" ))


#Meta URLs
clp_meta_url <- map_dfr(clp_Q_site_nums, create_meta_url)%>%
  as.data.frame()
bigt_meta_url <- map_dfr(bigt_Q_site_nums, create_meta_url)%>%
  as.data.frame()

#Data URLs
clp_data_url <- map_dfr(clp_Q_site_nums, create_data_url)%>%
  as.data.frame()
bigt_data_url <- map_dfr(bigt_Q_site_nums, create_data_url)%>%
  as.data.frame()

```

# Getting metadata

```{r metadata}


get_station_meta <- function(site_meta_url, site_number){
  
  request <- GET(url = site_meta_url)
  total_list <-content(request) 
  
 sensor_list <- total_list[["stationSummaries"]][[1]][["dataTypes"]]

   
  station_meta <- as.data.frame(do.call(rbind, sensor_list)) %>%
    mutate(name = as.character(name))%>%
    distinct(name)%>%
    mutate(sensor_list_num = row_number())%>%
    pivot_wider( names_from = "name", values_from = "sensor_list_num")%>%
    mutate(id = total_list[["stationSummaries"]][[1]][["id"]], 
           numid = total_list[["stationSummaries"]][[1]][["numId"]], 
           name = total_list[["stationSummaries"]][[1]][["name"]],
           elevation = total_list[["stationSummaries"]][[1]][["elevation"]],
           lat = total_list[["stationSummaries"]][[1]][["latitude"]],
           long = total_list[["stationSummaries"]][[1]][["longitude"]], 
           site_num = site_number)

  Sys.sleep(1)  

  return(station_meta)
}


```


## Getting meta

```{r meta grab}

#maps to get all metadata/ location of all sensors within JSON
clp_station_meta <- map2_dfr(clp_meta_url$site_url, clp_meta_url$site_number, get_station_meta)
bigt_station_meta <- map2_dfr(bigt_meta_url$site_url, bigt_meta_url$site_number, get_station_meta)

#create a total meta_df that can be referenced in downloading functions later on
final_meta <- rbind(clp_station_meta, bigt_station_meta)
```

# Q pull

This section will focus on downloading all the Q data available in the CLP and BIGT watershed available on the NovaStar site
## Functions

```{r Q grab function}

#This function actually breaks down the list for a given site into the datetime and value components
unlist_q_data <- function(i){
 unlist(discharge_data[[i]])
}

 

download_q <- function(site_url, site_number) {
  
  #create request to novastar website using url created 
  request <- GET(url = site_url)
  
  #gives content of httr pull
  total_list <- content(request)
  
  #find list number where q is located
  site_meta <- filter(final_meta, numid == site_number)
  
  Q_sensor_num <-  as.numeric(site_meta$DischargeRiver[1]) 
  
    # find list where discharge data is stored
    
  discharge_data <- total_list[["stationSummaries"]][[1]][["ts"]][[Q_sensor_num]][["data"]]
  
  
  q_df <- map_dfr(seq(1, length(discharge_data), 1), unlist_q_data)%>%
    mutate(numid = site_number)
  
  
  return(q_df)
  
   Sys.sleep(2)
}

test_site_url <- "https://larimerco-ns5.trilynx-novastar.systems/novastar/data/api/v1/stationSummaries?forOperatorStationDashboard=true&stationNumId=11531&periodStart=2022-01-25T13:59:00-07:00&periodEnd=2023-01-26T13:59:00-07:00"
 test_site_number <- "11531"
#
 
 test_q_df <- download_q(site_url = test_site_url, site_number = test_site_number)
 
# df_11531 <- download_q(site_url = clp_data_url_test$site_url[1],site_number = clp_data_url_test$site_number[1])
# df_11530 <- download_q(site_url = clp_data_url_test$site_url[2],site_number = clp_data_url_test$site_number[2])

```

## Pulling the Q

```{r}

#maps to get all metadata/ location of all sensors within JSON
clp_data_url_test <- head(clp_data_url, 2)%>%
  rename(site_number = site_num)

clp_q_station_data <- map2_dfr(clp_data_url_test$site_url, clp_data_url_test$site_number, download_q)

bigt_q_station_data <- map2_dfr(bigt_meta_url$site_url, bigt_meta_url$site_num, get_station_meta)

```


## Check the Q
 I'd recommend going to https://larimerco-ns5.trilynx-novastar.systems/novastar/operator/#/stationDashboard/100
 to double check and make sure the data looks similar to the sites you pulled
 
```{r}

test_df_q<- test_q_df%>%
  mutate(nice_dt = substr(dt, 1, nchar(dt)-9),
    datetime = as.POSIXct(dt, format = "%Y-%m-%dT%H:%M"), 
         q_cfs = as.double(v) )

plot_test_Q <- test_df_q%>%
  ggplot(aes( x= datetime, y = q_cfs))+
  geom_line()+
  theme_bw()+
  facet_wrap(~numid)
plot(plot_test_Q)



final_df_q<- clp_q_station_data%>%
  mutate(nice_dt = substr(dt, 1, nchar(dt)-9),
    datetime = as.POSIXct(dt, format = "%Y-%m-%dT%H:%M"), 
         q_cfs = as.double(v) )

plot_test_Q <- final_df_q%>%
  ggplot(aes( x= datetime, y = q_cfs))+
  geom_line()+
  theme_bw()+
  facet_wrap(~numid)
plot(plot_test_Q)


```
