---
title: "CamPk Reservoir Report 2022"
author: "Sam Struthers"
date: "2022-12-30"
output: html_document
---

```{r echo = FALSE}

tar_load(unique_chla)
tar_load(campaign_yr_breakdown)
tar_load(days_percent_meso_eutrophic)
tar_load(chla_no3_longitudinal_graphs)
tar_load(main_study_reservoirs_time_dotplot)
tar_load(site_map)
```

# 2022 Cameron Peak Reservoir Report

This document provides all the figures and analysis that we have completed during our Cameron Peak Fire Reservoir study in 2021 and 2022.

## Overview map

```{r}
site_map
```

# Summary Stats

Our sampling was broken into 3 campaigns: - Mainstem, outlined by FCGOV (XXX) - Reservoir, five primarily reservoirs, their outflows and some inflow sites - Tributaries, outlined by RMRS collaborators ISCO, to minimize the frequency of tributary sampling, four auto samplers were installed to collect "black water events"

```{r}
#Breaks down the number of samples per campaign
summary(campaign_yr_breakdown)
# breaks down the number of unique chla samples per site and per year
summary(unique_chla)
# Breaks down the number of sampling days per season that a site was mesotrophic (chla>2.6) or eutrophic (chla >8). It also displays the percent of sampling days in this classification  
summary(days_percent_meso_eutrophic)
```

# Longitudinal Plots

```{r}

chla_no3_longitudinal_graphs$chambers_plot


chla_no3_longitudinal_graphs$southfork_plot


chla_no3_longitudinal_graphs$mainstem_plot



```

##Study Reservoirs Chl-a

In comparison to last year, we saw an increase in chlorophyll-a levels. This increase was pronounced in burned reservoirs such as Chambers, Peterson and Barnes Meadow. We also saw an increase in levels in Joe Wright and Long Draw but the increases were less significant.

The graph below shows reservoirs colored by increasing burn severity from blue to red.

```{r}


main_study_reservoirs_time_dotplot



```
