---
title: "Download and Prepare Upper CLP Remote Sensing Data"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE)

# list packages for script
packages <- c("tidyverse",
              "googledrive",
              "feather",
              "sf")

# load package loader/installer
package_loader <- function(x) {
    if (x %in% installed.packages()) {
      library(x, character.only = TRUE) 
    } else {
      install.packages(x)
      library(x, character.only = TRUE)
    }
}

# use base-r to apply package loader to package list
invisible(lapply(packages, package_loader))

# point to rs data directory
rs_dir <- "data/RS/"
# and to spatial directory
spat_dir <- "data/spatial/all_study_waterbodies/"
dump <- "~/Desktop/clp_rs/"
```

# Purpose

## Download CLP data from Drive

There are two CLP files in the Drive, we'll grab them both, even though this workflow
will only use the subset of CLP data which contains the 7 study lakes. I'm getting
{curl} errors with this, so I'm just adding to the RS folder manually from the 
Drive folder. 

```{r}
# drive_auth("therossyndicate@gmail.com")
# 
# # get list of Drive files
# files <- drive_ls(path = "NW_CLP_for_analysis", pattern = ".feather")
# 
# # and subset for the CLP files
# files <- files[grepl("CLP", files$name), ]
# 
# # and download to the rs_dir
# download <- function(filename, dump_path) {
#   drive_download(file = filename, path = dump_path, overwrite = T)
# }
# 
# map2(files$name, rs_dir, download)
```


## Load all data and prep for project

Here, we'll just load in the feather files we just downloaded.

```{r}
clp_rs <- read_feather(file.path(rs_dir, "CLP_point_DSWE1_for_analysis_2023-12-08.feather"))
ross_clp_rs <- read_feather(file.path(rs_dir, "ROSS_CLP_point_DSWE1_for_analysis_2023-12-08.feather"))
```

And then we'll subset the CLP RS dataset for the 7 CLP study lakes, Comanche and
Hourglass weren't in the ROSS subeset. 

```{r}
clp_spat <- read_sf(file.path(spat_dir, "cpf_waterbodies.shp")) %>% 
  rename(GNIS_Name = gnis_nm)

clp_list <- clp_spat %>% 
  st_drop_geometry() %>% 
  select(GNIS_Name)

clp_rs <- left_join(clp_list, clp_rs)
```

## Save that file for next steps

```{r}
write_feather(clp_rs, file.path(rs_dir, "CPF_subset_DSWE1_RS_2023-12-08.feather"))
```

