---
title: "Download and Prepare Upper CLP Remote Sensing Data"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE)

# list packages for script
packages <- c("tidyverse",
              "googledrive",
              "feather",
              "sf")

# load package loader/installer
package_loader <- function(x) {
    if (x %in% installed.packages()) {
      library(x, character.only = TRUE) 
    } else {
      install.packages(x)
      library(x, character.only = TRUE)
    }
}

# use base-r to apply package loader to package list
invisible(lapply(packages, package_loader))

# point to rs data directory
rs_dir <- "data/RS/"
# and to spatial directory
spat_dir <- "data/spatial/all_study_waterbodies/"
```

# Purpose

This script just grabs the RS data specific to the CPF project and collates a new
file with the 7 reservoirs we care about.

## Download CLP data from Drive

There are two CLP files in the Drive, we'll grab them both, even though this workflow
will only use the subset of CLP data which contains the 7 study lakes. I'm getting
{curl} errors with this, so I'm just adding to the RS folder manually from the 
Drive folder. 

```{r}
# drive_auth("therossyndicate@gmail.com")
# 
# # get list of Drive files
# files <- drive_ls(path = "NW_CLP_for_analysis", pattern = ".feather")
# 
# # and subset for the CLP files
# files <- files[grepl("CLP", files$name), ]
# 
# # and download to the rs_dir
# download <- function(filename, dump_path) {
#   drive_download(file = filename, path = dump_path, overwrite = T)
# }
# 
# map2(files$name, rs_dir, download)
```


## Load all data and prep for project

Here, we'll just load in the feather file for CLP data we just downloaded.

```{r}
clp_rs <- read_feather(file.path(rs_dir, "CLP_point_DSWE1_for_analysis_2023-12-08.feather"))
```

And then we'll subset the CLP RS dataset for the 7 CLP study lakes, Comanche and
Hourglass weren't in the ROSS subset, using the shapefile of CPF waterbodies.

```{r}
# load spatial data
clp_spat <- read_sf(file.path(spat_dir, "cpf_waterbodies.shp")) %>% 
  rename(GNIS_Name = gnis_nm)

# drop geo, just keep GNIS name
clp_list <- clp_spat %>% 
  st_drop_geometry() %>% 
  select(GNIS_Name)

# left join clp list with rs data
clp_rs <- left_join(clp_list, clp_rs)

# loopy check
unique(clp_rs$GNIS_Name)
length(unique(rs_jun_sep$COMID)) #just in case there are any with same name in dataset
```

## Save that file for next steps

```{r}
write_feather(clp_rs, file.path(rs_dir, "CPF_subset_DSWE1_RS_2023-12-08.feather"))
```

