---
title: "Visualize RS temperature"
author: "ROSSyndicate"
date: "`r Sys.Date()`"
output: html_document
---

# Purpose

This script pulls in the data created in "00_download_RS_and_prep.Rmd", passes some
very high-level QAQC, then visualizes temperature and some of the band data as a
proxy for clarity.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE)

# list packages for script
packages <- c("tidyverse",
              "ggthemes",
              "feather")

# load package loader/installer
package_loader <- function(x) {
    if (x %in% installed.packages()) {
      library(x, character.only = TRUE) 
    } else {
      install.packages(x)
      library(x, character.only = TRUE)
    }
}

# use base-r to apply package loader to package list
invisible(lapply(packages, package_loader))

# point to rs data directory
rs_dir <- "data/RS/"


# basic theme for all ggplots
ROSS_theme = theme_bw() + #or theme_few()
    theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 24),
          axis.title = element_text(hjust = 0.5, size = 16),
          strip.text = element_text(size = 16)) 

```

## Load data and high-level QAQC

Read in the file created in "00_download..."

```{r}
rs <- read_feather(file.path(rs_dir, "CPF_subset_DSWE1_RS_2023-12-08.feather")) %>% 
  mutate(surf_temp_degC = med_SurfaceTemp - 273.15) %>%  #convert from Kelvin
  filter(pCount_dswe1 > 10) # filter for rs data with at least 10 dswe1 pixels

# filter Jun-Sep
rs_jun_sep <- rs %>% 
  filter(between(month(date), 6, 9)) %>% 
  # and where the pixel-specific cloud proportion is 0
  # the thermal band is very sensitive to clouds, even when they are adjacent
  # to masked pixels.
  filter(prop_clouds == 0) %>% 
  mutate(GNIS_Name = str_replace(GNIS_Name, "Lake", "Reservoir"))
```

To cohere with CPF color, we'll pull in the color scale and add in the two unburned
reservoirs as green:

```{r}
#Color for waterbodies, matches burn severity
res_colors <- c("Barnes Meadow Reservoir" = "#D55E00", 
                "Peterson Reservoir" ="#E69F00", 
                "Chambers Reservoir" = "#F0E442", 
                "Joe Wright Reservoir" = "#56B4E9", 
                "Long Draw Reservoir" = "#0072B2",
                "Comanche Reservoir" = "#0072B2",
                "Hourglass Reservoir" = "#0072B2")

```

We're also going to factor the names using this burn severity scale:

```{r}
rs_jun_sep <- rs_jun_sep %>% 
  mutate(GNIS_Name = factor(GNIS_Name, levels = c("Barnes Meadow Reservoir", 
                                                  "Peterson Reservoir",
                                                  "Chambers Reservoir", 
                                                  "Joe Wright Reservoir",
                                                  "Long Draw Reservoir",
                                                  "Comanche Reservoir",
                                                  "Hourglass Reservoir")))
```

And visualize the data

```{r}
ggplot(rs_jun_sep, aes(x = date, y = surf_temp_degC, color = GNIS_Name)) +
  geom_point() +
  facet_wrap(~ GNIS_Name, ncol = 3) +
  scale_color_manual(values = res_colors) +
  ROSS_theme
```

There is a scene-level outlier (seen in Barnes and Champbers) - these are from the 
same scene and there is no other info that would lead us to throw these out, but
nonetheless, this is suspect. Going to throw out for now.

```{r}
rs_jun_sep <- rs_jun_sep %>% 
  filter(system.index != "1_2_LT05_034032_20110608")

ggplot(rs_jun_sep, aes(x = date, y = surf_temp_degC, color = GNIS_Name)) +
  geom_point() +
  facet_wrap(~ GNIS_Name, 
             ncol = 4,
             labeller = label_wrap_gen(width = 15, multi_line = T)) +
  scale_color_manual(values = res_colors) +
  ROSS_theme +
  theme(legend.position = "none") +
  labs(x = NULL,
       y = "Uncorrected Surface Temperature Estimate (deg C)",
       title = "Remotely-Sensed Surface Temperature at CPF Lakes")

ggsave(file.path(rs_dir, "figs/RS_uncorr_temp_CPF_lakes.png"),
       height = 8,
       width = 12,
       dpi = 300,
       units = "in")

```

## Plots of relative clarity

Using the measure of Red:Blue as a non-linear proxy, we can estimate clarity as
a relative measure:

```{r}
rs_jun_sep_clarity <- rs_jun_sep %>% 
  # drop any obs where there is a flag for the correction
  filter(if_all(c(flag_Red_7, flag_Blue_7), ~ . == "")) %>%
  # create a clarity proxy based on NW matchups
  mutate(clarity_proxy = med_Red_corr7/med_Blue_corr7) 
```

and plot with axes to be 'higher clarity' (lower ratio) and 'lower clarity' 
(higher ratio).

```{r}
ggplot(rs_jun_sep_clarity, aes(x = date, y = clarity_proxy, color = GNIS_Name)) +
  geom_point() +
  facet_wrap(~ GNIS_Name, 
             ncol = 4,
             labeller = label_wrap_gen(width = 15, multi_line = T)) +
  scale_color_manual(values = res_colors) +
  ROSS_theme +
  scale_y_continuous(breaks = c(0.5, 2.0), labels = c("higher\nclarity", "lower\nclarity")) +
  theme(legend.position = "none", 
        panel.grid = element_line(linewidth = 0),
        axis.text.y = element_text(size = 14)) +
  labs(x = NULL,
       y = "Simple clarity proxy (Red:Blue)",
       title = "Remotely-Sensed Clarity Proxy at CPF Lakes")

ggsave(file.path(rs_dir, "figs/RS_clarity_proxy_CPF_lakes.png"),
       height = 8,
       width = 12,
       dpi = 300,
       units = "in")
```

