---
title: "Correlation and Linear Modeling"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")


```

# Linear Modeling of Nutrient and Algal dyanmics

## Goals of this document:

-   Create function that makes a linear model between all water quality variables

-   Run function on subsets

    -   Campaigns (Res, mainstem, different res systems)

    -   Sites

    -   Seasons

```{r import}
long_df <- read_feather("data/field_chemistry/cleaned/res_all_chem")
# Load data
reservoir_chemistry <- read_feather("data/field_chemistry/cleaned/reservoir_chem_2021_2022.feather")
# Load metadata for units
meta_units_table <- read_csv("data/field_chemistry/Poudre_Portal_Data/Units_Cam_Peak.csv")
fcgov_mainstem_df <- read_feather("data/field_chemistry/cleaned/fcgov_mainstem")

reservoir_chemistry_long <- reservoir_chemistry%>%
  pivot_longer(cols = c(ChlA, Turbidity, TSS, pH,ANC, Na, NH4, K, Mg, Ca, F, Cl, PO4, SO4, SC,NO3, DOC, DTN),names_to = "param", values_to = "value")

```

## Linear Model Function

### Cleaning Model
```{r}

extract_slope <- function(sens_model){
  
  tidy(sens_model) %>%
    mutate(slope = sens_model$estimates)
  
}
```


```{r}



reservoir_chemistry_nested <- reservoir_chemistry_long%>%
  filter(Year > 2020& !is.na(value)& site_code %in% mainstem_res_set)%>%
  arrange(Date)%>%
  select(site_code, Date,param, value, Year, location, watershed, status, season )%>%
  group_by(site_code, param)%>%
  nest()

res_system_chem_models <- reservoir_chemistry_nested%>%
  mutate(sens_model = map(data, ~ sens.slope(.x$value)), 
         tidy_sens = map(sens_model, extract_slope)) %>%
  unnest(tidy_sens) %>%
  select(site_code, param, p.value, slope) %>%
  mutate(trend = ifelse(p.value < 0.01, 'yes', 'no'))%>%
  left_join(Sites, by = "site_code")
  

res_only_models <- filter(res_system_chem_models, site_code %in% mainstem_Res_only& trend == "yes")%>%
  filter(param != "ANC")
 
ggplot(res_only_models,aes(x = param, y = slope, color = site_code)) + 
## add a dashed balck line at 0
geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_point() + 
  theme_few() + 
  scale_color_manual(values = colorsBS_site_code ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.pos = c(0.8, 0.8))

ggplot(filter(res_system_chem_models, param %nin% c("ANC", "SC")),aes(x = param, y = slope, color = trend)) + 
## add a dashed balck line at 0
geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_point() + 
  theme_few() + 
  scale_color_manual(values = c( "yes"= "green",  "no" = "red" ) ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.pos = c(0.8, 0.8))+
  facet_wrap(~location, nrow = 3, scales = "free")

```
 
 ## t-test for measured parameters
```{r}
# create a data frame with all the parameters
all_param_df <- reservoir_chemistry_long%>%
  filter(Year > 2020& !is.na(value)& site_code %in% mainstem_res_set)%>%
  arrange(Date)%>%
  select(site_code, Date,param, value, Year, location, watershed, status, season )%>%
  group_by(site_code, param)%>%
  nest()

  # using all_param_df, create a data frame map over the data column and run a t-test
  # on the value column
  # save the t-test results in a new column called t_test
  # save the p-value in a new column called p_value
  # save the t-statistic in a new column called t_statistic
  # save the degrees of freedom in a new column called df
  # save the mean of the value column in a new column called mean
  # save the standard deviation of the value column in a new column called sd
  # save the number of observations in a new column called n

t_test_df <- all_param_df%>%
  mutate(t_test_model = map(data, ~ t.test(.x$value)),
          t_test = map(t_test_model, ~ .$statistic),
          p_value = map(t_test_model, ~ .$p.value),
         mean = map(data, ~ mean(.x$value)),
         sd = map(data, ~ sd(.x$value)),
         n = map(data, ~ length(.x$value)))%>%
  mutate(t_test = as.numeric(t_test),
         p_value = as.numeric(p_value),
         # t_statistic = as.numeric(t_statistic),
         # df = as.numeric(df),
         mean = as.numeric(mean),
         sd = as.numeric(sd),
         n = as.numeric(n),
         trend = ifelse(p_value < 0.01, 'yes', 'no'))%>%
  select(site_code, param, p_value, mean, sd, n, trend)

ggplot(filter(t_test_df, param %nin% c("ANC", "PO4", "TSS", "Turbidity")) , aes(x = site_code, y = mean, color = site_code)) + 
## add a dashed black line at 0
geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_point() + 
  theme_few() + 
  facet_wrap(~param, scales = "free")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.pos = c(0.8, 0.1))



```
 
 
 #Old testing stuff
```{r}

linear_model_two_parameters<- function(parameter1, parameter2){
  
  subset_df <- long_df%>%
    filter(Parameter %in% c(parameter1, parameter2))%>%
    pivot_wider( names_from = Parameter, values_from = Measurement)%>%
    dplyr::select(x= parameter1, y = parameter2)%>%
    na.omit()
  
    chem_lm <- lm(x ~ y, data = subset_df)
  
  # summary of lm created
  # this is where coefficients will be pulled from
  
  # intercept == b
  # logH == a
  chem_summary <- summary(chem_lm)
  
  # pulling coefficients in to results data frame
    lm_results <- tibble(
      x = parameter1, 
      y = parameter2, 
      intercept = chem_summary$coefficients[1,1], 
      slope = chem_summary$coefficients[2,1], 
      r2 =chem_summary$r.squared
    )
      

  return(lm_results)
}
plot(chem_lm)


parameter1 <- unique(long_df$Parameter[1])
parameter2 <- unique(long_df$Parameter)

all_sites_all_param_lm <- map2(parameter1, parameter2, linear_model_two_parameters)%>%
  list_rbind()%>%
  dplyr::select(chla = x, param2 = y , int = intercept, m = slope, r2)

view(all_sites_all_param_lm)
```


## Plotting Linear models
```{r}

#plot linear models as line graphs using the and int values from the linear model data frame
# using the package ggplot2





```

## Function 

```{r}

site_linear_model_two_parameters<- function(parameter2){

  parameter1 <- unique(long_df$Parameter[1])
site_name <- "CBRR"

  subset_df <- long_df%>%
    filter(site_code %in% site_name)%>%
    filter(Parameter %in% c(parameter1, parameter2))%>%
    pivot_wider( names_from = Parameter, values_from = Measurement)%>%
    dplyr::select(x= parameter1, y = parameter2)%>%
    na.omit()
  
    chem_lm <- lm(x ~ y, data = subset_df)
  
  # summary of lm created
  # this is where coefficients will be pulled from
  
  # intercept == b
  # logH == a
  chem_summary <- summary(chem_lm)

  if(is.na(chem_summary$coefficients[2,1])){
    next
  }
  

  # pulling coefficients in to results data frame
    lm_results <- tibble(
      x = parameter1, 
      y = parameter2, 
      intercept = chem_summary$coefficients[1,1], 
      slope = chem_summary$coefficients[2,1], 
      r2 =chem_summary$r.squared
    )
      

  return(lm_results)
}
parameter2 <- unique(long_df$Parameter)
parameter2 <- "PO4"
tester <- site_linear_model_two_parameters("PO4")

indv_sites_test_param_lm <- map(parameter2, site_linear_model_two_parameters)%>%
  dplyr::select(chla = x, param2 = y , int = intercept, m = slope, r2)



```


## Correlation testing

```{r}

parameter2 <- unique(long_df$Parameter)

cor_by_site <- function(parameter2){
  
  cor_results <- tibble()
  for(i in 1:length(unique(long_df$Parameter))){
 parameter1 <- unique(long_df$Parameter[i])
site_name <- "CBRR"

  subset_df <- long_df%>%
    filter(site_code %in% site_name)%>%
    filter(Parameter %in% c(parameter1, parameter2))%>%
    pivot_wider( names_from = Parameter, values_from = Measurement)%>%
    dplyr::select(x= parameter1, y = parameter2)%>%
    na.omit()
  
  cor_by_param <- cor(subset_df$x, subset_df$y)
  
  cor_indv <- tibble(
      x = parameter1, 
      y = parameter2, 
      cor_value = cor_by_param
    )
  cor_results <- rbind(cor_indv, cor_results)
  }
  return(cor_results)
  
}




test_cleaned <- tester%>%
  distinct(cor_value, .keep_all = TRUE)%>%
  filter(!is.na(cor_value)& cor_value != 1)%>%
  mutate(cor_value = format(cor_value, scientific = FALSE), 
         cor_correct = abs(as.double(cor_value)))



```

## Correlation across all sites

```{r}


cor_all_sites <- function(parameter2){
  

  cor_results <- tibble()
  
  for(i in 1:length(unique(long_df$Parameter))){
 parameter1 <- unique(long_df$Parameter[i])


  subset_df <- long_df%>%
    filter(Parameter %in% c(parameter1, parameter2))%>%
    pivot_wider( names_from = Parameter, values_from = Measurement)%>%
    dplyr::select(x= parameter1, y = parameter2)%>%
    na.omit()%>%
    rowid_to_column()
  
  cor_by_param <- cor(subset_df$x, subset_df$y)
  
  cor_indv <- tibble(
      x = parameter1, 
      y = parameter2, 
      cor_value = cor_by_param, 
      n = max(subset_df$rowid)
    )
  cor_results <- rbind(cor_indv, cor_results)
  }
  return(cor_results)
  
}
parameter2 <- unique(long_df$Parameter)
all_sites_cor<- map(parameter2, cor_all_sites)%>%
  list_rbind()

all_sites_cor_clean <- all_sites_cor %>%
  distinct(cor_value, .keep_all = TRUE)%>%
  filter(!is.na(cor_value) & x != y)%>%
  mutate(cor_correct = abs(as.double(cor_value)), 
         cor_value = format(cor_value, scientific = FALSE))%>%
  filter(n >100)

```

## Pariwise Plots

```{r}

norm_df <- long_df%>%
  filter(site_code %in% all_res_system)%>%
  dplyr::select(Parameter, Measurement, FCW_Number)%>%
  pivot_wider(names_from = Parameter,
              values_from = Measurement)%>%
  dplyr::select(-c(FCW_Number, Fe, Mn, P, Al, pH, ANC, Mg, TSS, SC))

pairs(norm_df)


  ggplot(norm_df, aes(x = NH4, y = DOC))+
    geom_point()+
    geom_smooth()+
    theme_bw(base_size = 15)


chla_site_pairs <- long_df%>%
  filter(site_code %in% c("JOER", "JOEI", "CBRI","CBRR","CHD"))%>%
  pivot_wider(names_from = Parameter,
              values_from = Measurement)%>%
  filter(!is.na(ChlA))%>%
  filter(Date != "2022-06-01")%>%
  dplyr::select(Date, ChlA, site_code)%>%
  pivot_wider(names_from = site_code, 
              values_from = ChlA)



pairs(chla_site_pairs)


  ggplot(chla_site_pairs, aes(x = BRNR, y = CBRR))+
    geom_point()+
    geom_smooth(method = "lm")+
    theme_bw(base_size = 15)




for(i in 1:length(chla_site_pairs)){
  
  cor_by_param <- cor(subset_df$x, subset_df$y)
  
  cor_indv <- tibble(
      x = parameter1, 
      y = parameter2, 
      cor_value = cor_by_param
    )
  cor_results <- rbind(cor_indv, cor_results)
  
}


```

