---
title: "Longitudinal mapping of Reservoir -> River Connection"
author: "Sam Struthers"
format: html
editor: visual
self-contained: true
---

# Goals

This document is to work on graphs related to nutrients from Reservoirs/ mainstem

### Importing

Loading packages and creating lists of sites based on location/grouping

```{r}
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")


reservoir_chemistry <- read_feather("data/field_chemistry/cleaned/reservoir_chem_2021_2022.feather")%>%
  mutate(location = factor(location, levels = c("Inflow","Reservoir", "Outflow", "Stream", "Mainstem")))


library(basemapR)


```

### Get lines and points

```{r}

  up_and_down_sites <- tibble(site_code = ratio_sites_names_all)%>%
  mutate(site_one= str_extract(site_code, "^[A-Z]+"),
         site_two = str_extract(site_code, "[A-Z]+$"),
         site_ratio = site_code) %>%
  left_join(Sites, by = c("site_one" = "site_code")) %>%
  dplyr::rename(lat1 = Lat, long1 = Long) %>%
  left_join(Sites, by = c("site_two" = "site_code")) %>%
  dplyr::rename(lat2 = Lat, long2 = Long) %>%
  select(site_ratio, lat1, long1, lat2, long2)

up_site_lines <- select(up_and_down_sites, site_ratio, Long = long1, Lat = lat1)%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)
down_site_lines <- select(up_and_down_sites, site_ratio, Long = long2, Lat = lat2)%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)

site_lines <-st_union(up_site_lines, down_site_lines)%>%
  filter(site_ratio == site_ratio.1)%>%
  st_cast(to = "LINESTRING")%>%
  dplyr::select(site_code = site_ratio, geometry)


site_points <- Sites%>%
  dplyr::select(site_code, Lat, Long)%>%
  filter(site_code %in% c(all_res_system, mainstem_sites, "BEAV"))%>%
  st_as_sf(coords = c("Long", "Lat"), crs = 4326)
```

### Get lines as flowlines

```{r}

# get flowlines
clp  <- get_huc(id = '10190007', type = "huc08")
clp_flowlines <- get_nhdplus(AOI = clp, 
                             realization='flowline')





ratio_flowlines<- st_read("data/spatial/ratio_flowlines_widest.kml")%>%
  st_transform(crs = 4326)%>%
  select(site_code = Name)%>%
  st_cast("LINESTRING")

mapview::mapviewOptions(fgb = FALSE)

mapview::mapview(ratio_flowlines)+
  mapview::mapview(site_points)

```



## Data frame creation

Create dataframe for ratio mapping and

```{r}


res_2021 <- filter(reservoir_chemistry, site_code %in% jw_chambers_complex & Year == 2021)

# filter reservoir chemistry for 2022
# only use sites from all_res_system and mainstem_sites

all_system_2022 <- filter(reservoir_chemistry, site_code %in% c(all_res_system, mainstem_sites, "BEAV") & Year == 2022)


```

# Ratio Map

## Function to get ratios

This section organizes the data by site and calculates ratios between upstream and downstream sites.

```{r}



get_ratios_2022 <- function(nutrient){

  
  nr <- all_system_2022%>%
    dplyr::select(date = Date,
         site_code,
         all_of(nutrient))%>%
  pivot_wider(names_from = site_code, values_from = nutrient)%>%
    filter(date %nin% genomic_dates)
  ## Remove rows were all columns other than Date are NA
 nr_no_na_rows <- nr[rowSums(is.na(nr)) != (ncol(nr)-1), ]%>%
   thicken(interval = "week", 
           start_val = as.Date("2022-05-30"))
# remove the date column and consolidate the rows by date_week
  nr_concise <- nr_no_na_rows%>%
    select(-date)%>%
    pivot_longer(cols = c(-date_week), 
                 names_to = "site",
                 values_to = "value")%>%
    drop_na()%>%
  pivot_wider(names_from = site, values_from = value)
  

    
  nr_final_df <- nr_concise%>%
    mutate(JOEI_JOER  = (JOER/JOEI), 
           JOER_CBRI = (CBRI/JOER), 
           CBRI_CBRR = (CBRR/CBRI), 
           CBRR_CHD = (CHD/CBRR), 
           CHD_JWC = (JWC/CHD), 
           BRNR_BMD = (BMD/BRNR), 
           BMD_JWC = (JWC/BMD), 
           PTRR_PTRO = (PTRO/PTRR), 
           PTRO_PJW = (PJW/PTRO), 
           LNGR_LNGO = (LNGO/LNGR), 
           LNGO_PJW = (PJW/LNGO), 
           JWC_SLEP = (SLEP/JWC),
           PJW_SLEP = (SLEP/PJW), 
           SLEP_PBR = (PBR/SLEP), 
           PBR_PSF = (PSF/PBR), 
           COMI_COMR = (COMR/COMI), 
           COMR_COMO = (COMO/COMR), 
           COMO_BEAV =  (BEAV/COMO) , 
           HORI_HORR = (HORR/HORI), 
           HORR_HORO = (HORO/HORR), 
           HORO_BEAV = (BEAV/HORO), 
           BEAV_SFM = (SFM/BEAV), 
           SFM_PSF = (PSF/SFM), 
           PSF_PNF = (PNF/PSF), 
           PNF_PBD = (PBD/PNF)
           )%>%
    pivot_longer(., cols = -date_week, names_to = "site_code", values_to = nutrient)
  
 return(nr_final_df)
   
}

```

## Join ratio and spatial

Functions make the point and ratio data spatial to be used for mapping

```{r}



make_line_ratio_spatial_flowlines <- function(nr_final_df, nutrient){
  
  nutrient_ratios_lines <- nr_final_df %>%
  inner_join(ratio_flowlines, by = "site_code")%>%
  st_sf()%>%
  dplyr::rename(ratio = nutrient )


return(nutrient_ratios_lines)
  
}

make_point_ratio_spatial <- function(nr_final_df){
  
  nutrient_ratios_points <- nr_final_df %>%
  inner_join(site_points, by = "site_code")%>%
  st_sf()


return(nutrient_ratios_points)
  
}




```

### layout 

```{r}

my_layout <- function() {
  tm_layout(
    bg.color = "white",
    legend.position = c("right", "bottom"),
    legend.title.size = 1,
    legend.text.size = 0.8,
    legend.frame = FALSE,
    legend.outside = TRUE,
    title.position = c("left", "top"),
    title.size = 1,
    title.margin = c(0, 0, 0, 20),
    title.adjust = 0.5,
    title.just = "left",
    title.text = text(paste("Week of 2022-05-30"), 
                      col = "black", cex = 1.2, fontface = "bold"))
}

```


## Plotting/ animation functions

This will create a plot for specific date_weeks in the data or animations for an entire year.

```{r}

chla_nr_df <- get_ratios_2022(nutrient = "ChlA")

nutrient_ratios_lines <- make_line_ratio_spatial_flowlines(nr_final_df = chla_nr_df, nutrient = "ChlA")%>%
# if percent_change is greater than 20, set to 20
  mutate(ratio = ifelse(ratio > 20, 20, ratio))


nutrient_ratios_points <- make_point_ratio_spatial(chla_nr_df)
test<- filter(nutrient_ratios_lines, site_code %in% ratio_sites_names_upper_select)%>%
  drop_na()

length(unique(test$date_week))

  #tm_shape(filter(nutrient_ratios_points, date_week == "2022-08-08"& site_code %in% c(mainstem_res_set, "JWC", "PJW", "SLEP")), name = "Sampling Locations")+
 select_upper_plot <- tm_shape(filter(nutrient_ratios_lines, site_code %in% ratio_sites_names_upper_select & date_week == "2022-06-06"), name = "Flow Lines")+
  tm_lines(col = "ratio", palette = "Greens", n = 5, contrast = c(0.5, 0.9),
           breaks = c(0, .5, 1, 2, 5, 10, 20),
           lwd = 2.5)+
   # tm_facets(as.layers = TRUE, free.coords = FALSE, free.scales.symbol.size = FALSE,
   #          nrow = 1, ncol = 1 )+
   tm_shape(filter(nutrient_ratios_points, site_code %in% sites_names_upper_select & date_week == "2022-06-06"), name = "Sampling Locations")+
  tm_bubbles(size = "ChlA", breaks = c(0, .5, 1, 2, 5, 10, 20))
    # tm_facets(as.layers = TRUE, free.coords = FALSE, free.scales.symbol.size = FALSE,
    #         nrow = 1, ncol = 1)+
  # add title in top left corner which is date_week


 #+tm_facets(along = "date_week", free.coords = FALSE, free.scales.symbol.size = FALSE,
            #nrow = 1, ncol = 1)
 select_upper_plot

tmap_leaflet( select_upper_plot , mode = "view")%>%
  addProviderTiles("Esri.WorldTopoMap") 


tmap_animation(tester, filename = "output/spatial/chla_tester_upper.gif", width = 1400, height = 800, delay = 15)
tmap_animation(tester_lines, filename = "output/spatial/chla_tester_lines.gif", width = 1200, height = 600, delay = 15)


#Functionalize! tbd later

avail_weeks <- unique(nutrient_ratios_points$date_week)

plot_ratios_one_week <- function(week, point_df, line_df, nutrient){
  return(map_plot)
}

season_animation<- function(point_df, line_df, nutrient){
  return(map_animation)
}
```

## Using ratio functions for plotting

```{r}
library(ggmap)
library(gganimate)


AOI_1 <- get_map(location = c(lon = 	-105.8364 , lat = 40.60038 ), zoom = 12,  maptype = "hybrid")

frames <- length(unique(filter(nutrient_ratios_lines, site_code %in% ratio_sites_names_upper_select)$date_week))-1

select_upper <- ggmap(AOI_1)+
  coord_sf(crs = st_crs(3857))+
  geom_sf(data = filter(nutrient_ratios_lines, site_code %in% ratio_sites_names_upper_select), aes(color = ratio, group = date_week), size = 1.5, inherit.aes = FALSE)+
  # set the color palette to be "Greens" and have breaks at 0, 0.5, 1, 2, 5, 10, 20
  scale_color_gradientn(colours = c("white", "red"), breaks = c(0, .5, 1, 2, 5, 10, 20))+
   geom_sf(data = filter(nutrient_ratios_points, site_code %in% sites_names_upper_select), aes(size = ChlA, group = date_week), alpha = .5, inherit.aes = FALSE)+
  coord_sf(crs = st_crs(4326))+
  transition_manual(date_week)+
 ggtitle('Year: {frame_time}',
           subtitle = 'Frame {frame} of {nframes}') +
  shadow_mark()
  

animation <- animate(select_upper, nframes = frames, fps = 2 )


ggmap(AOI_1)
?geom_sf()

get_map()


AIzaSyA0OuqJX1-vDClQ7I-C0Wh5lwV5UP4SIMI


```


# 2021 JW and Chamber's longitudinal data

## Functionalize plotting of means and SDs

```{r}


plot_long_jw_ch <- function(param, year = 2021,  title = FALSE){


  ratio_for_param <- filter(reservoir_chemistry, site_code %in% jw_chambers_complex & Year == year)%>%
    dplyr::select(all_of(param), Date, site_code)%>%
     pivot_wider(names_from = site_code, values_from = param)%>%
    drop_na()%>%
    mutate(JOEI_JOER = JOER/JOEI, 
           JOER_CBRI = CBRI/JOER,
           CBRI_CBRR = CBRR/CBRI,
           CBRR_CHD = CHD/CBRR)
  

  
# create a mean_2021 dataframe that has the mean of JOEI, JOER, CBRI, CBRR and CHD
#pivot longer and name the columns "site" and "value"
  lean_mean_machine <- ratio_for_param%>%
    pivot_longer(cols = c("JOEI", "JOER", "CBRI", "CBRR", "CHD"),
                 names_to = "site",
                 values_to = "value")%>%
    group_by(site)%>%
    summarise(mean = mean(value), 
              sd = sd(value))%>%
    ungroup()%>%
    mutate(site = factor(site, levels = c("JOEI", "JOER", "CBRI", "CBRR", "CHD")), 
           mean_plus_sd = mean + sd, 
           mean_minus_sd = mean - sd, 
           type = "mean")
  
  no_ratios <- ratio_for_param%>%
    pivot_longer(cols = c("JOEI", "JOER", "CBRI", "CBRR", "CHD"),
                 names_to = "site",
                 values_to = "value")%>%
     mutate(site = factor(site, levels = c("JOEI", "JOER", "CBRI", "CBRR", "CHD")))

 if(title == TRUE){
 plot <- ggplot(lean_mean_machine, aes(x = site))+
   geom_point(data = no_ratios, aes(y = value, color = site), alpha  = .6)+
   geom_ribbon(aes(ymin = mean_minus_sd, ymax = mean_plus_sd, 
                  group = type), alpha = 0.2)+
   geom_point(aes(y = mean))+
   geom_line(aes( y = mean, group = type))+
   scale_color_manual(values = colorsBS_in_order)+
   theme_few(base_size = 20) +
   labs(x = "Site (Upstream to Downstream)", 
        y = param)+
   #add the year in the top left quadrant of the plot
    #annotate("text", x = 1, y = 1.5, label = year, size = 10)+
    theme(legend.position = "none")
}
  
  if(title == FALSE){
 plot <- ggplot(lean_mean_machine, aes(x = site))+
   geom_point(data = no_ratios, aes(y = value, color = site), alpha  = .6)+
   geom_ribbon(aes(ymin = mean_minus_sd, ymax = mean_plus_sd, 
                  group = type), alpha = 0.2)+
   geom_point(aes(y = mean))+
   geom_line(aes( y = mean, group = type))+
   scale_color_manual(values = colorsBS_in_order)+
   theme_few(base_size = 20) +
   labs(x = "Site (Upstream to Downstream)", 
        y = param)+
        
        #remove x axis labels and title
      theme(axis.text.x = element_blank(),
            axis.ticks.x = element_blank(),
            axis.title.x = element_blank())+
    theme(legend.position = "none")
}
 return(plot)
}
```

## Param long 2021 JW CH plots

```{r}
# run the function for each parameter: ChlA, NO3, PO4, NH4, DOC, DTN, pH, SO4, K
# save each plot as a variable

no3 <- plot_long_jw_ch_2021(param = "NO3")
nh4 <- plot_long_jw_ch_2021(param = "NH4")
doc <- plot_long_jw_ch_2021(param = "DOC")
dtn <- plot_long_jw_ch_2021(param = "DTN")
ph <- plot_long_jw_ch_2021(param = "pH")
so4 <- plot_long_jw_ch_2021(param = "SO4")
k <- plot_long_jw_ch_2021(param = "K", title = TRUE)
chlA <- plot_long_jw_ch_2021(param = "ChlA", title = TRUE)
tss <- plot_long_jw_ch_2021(param = "TSS")
turbidity <- plot_long_jw_ch_2021(param = "Turbidity", title = TRUE)

#arrange the plots in a grid
ggarrange(no3, nh4, doc, dtn, ph, so4, k, chlA, ncol = 2, nrow = 4)



no3_2021 <- plot_long_jw_ch(param = "NO3", year = 2021)+
            ylim(-.1,2)
no3_2022 <- plot_long_jw_ch(param = "NO3", year = 2022, title = TRUE)
chla_2021 <- plot_long_jw_ch(param = "ChlA", year = 2021)+
            ylim(-.25, 10)
chla_2022 <- plot_long_jw_ch(param = "ChlA", year = 2022, title = TRUE)

ggarrange(chla_2021, no3_2021, chla_2022, no3_2022, ncol = 2, nrow = 2)
ggsave("output/chla_no3_JW_CH_facet_mean_sd.jpg", width = 24, height = 16, dpi = 300)
```
