---
title: "Analysis and Figures"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("src/00_analysis_setup.R")
```

# Grab data

```{r}
#discrete sample data and location metadata from most recent pub
DOI = "10372690"
data_version = "v12.13.23b"
source("src/analysis_fxns/grab_zenodo_data.R")

all_params <- chem_units%>%
  pull(simple)
# sensor data
source("src/analysis_fxns/grab_sensor_data.R")

```


## Tidy discrete

```{r}
tidy_chem <- most_recent_chem%>%
  filter(Year > 2020)%>%
  left_join(time_data, by = "FCW_Number")%>%
  mutate(dt = case_when( !is.na(Time) ~ as.POSIXct(paste0(Date," ", Time), format = "%Y-%m-%d %H:%M"), 
                         TRUE ~ NA), 
         distance_upstream_km = case_when(site_code == "PFAL" ~ 73.9, TRUE ~ distance_upstream_km))%>%
  left_join(order_table, by = "site_code") 
#time data and site order now added to tidy chem and thus not needed
rm(time_data, order_table)

```
## Run above to get data loaded

```{r}
print("Data Successfully loaded for analysis")
```


# Reporting Calculations
These data and calculations will be included in the funder report to give an overview of how the system is changing year to year based on our study

## Chlorophyll a status

In cold water lakes (our study sites), mesotrophic levels are defined as between 2.6 and 8 µg/L, and eutrophic levels are greater than 8 µg/L. Under 2.6 µg/L is considered Oligotrophic. 
```{r}

chla_status_site_year <- tidy_chem%>%
  filter(!is.na(ChlA))%>%
  mutate(eu_status  = case_when(ChlA >= 2.6 &ChlA <= 8 ~ "Mesotrophic", 
                                ChlA > 8 ~ "Eutrophic",
                                ChlA < 2.6 ~ "Oligotrophic"))%>%
  group_by(site_code, Year, eu_status)%>%
  summarise(eu_stats = n())%>%
  ungroup()%>%
  pivot_wider(names_from = eu_status, values_from = eu_stats)%>%
  mutate_at(vars(-Year), ~replace(., is.na(.), 0))%>%
  rowwise()%>%
  mutate(total_samples = sum(c(Eutrophic, Mesotrophic, Oligotrophic)),
    perc_eu = round((Eutrophic/total_samples)*100, digits= 1), 
         perc_meso = round((Mesotrophic/total_samples)*100, digits= 1),
         perc_meso_eu = round(((Eutrophic+Mesotrophic)/total_samples)*100, digits= 1), 
        perc_oligo = round((Oligotrophic/total_samples) *100, digits= 1),
    Year = as.character(Year))


long_chla_status <- chla_status_site_year%>%
  select(site_code, Year, total_samples, perc_eu, perc_meso, perc_meso_eu, perc_oligo)%>%
  pivot_longer(cols = c(perc_eu, perc_meso, perc_meso_eu, perc_oligo), names_to = "category", values_to = "value" )

status_plot <- long_chla_status%>%
  filter(site_code %in% mainstem_Res_only )%>%
  ggplot(aes(x = Year, y = value,group = site_code, color =  site_code))+
  scale_color_manual(values = colorsBS_site_code)+
 geom_line()+
   geom_point()+
  theme_bw(base_size = 15)+
facet_wrap(~category)
plot(status_plot)



```

## chla stats

```{r}


chla_per_year <-tidy_chem%>%
  select(ChlA, Year, site_code, Date, watershed)%>%
  na.omit()%>%
  group_by(Year)%>%
  summarise(count_year = n())


chla_per_site_year <-tidy_chem%>%
  select(ChlA, Year, site_code)%>%
  na.omit()%>%
  group_by(Year, site_code)%>%
  summarise(n = n(), 
         mean = mean(ChlA), 
         median = median(ChlA))%>%
  ungroup()%>%
  dplyr::arrange(site_code,Year)

```

# Mean all params

Code to make SI tables for minimum and maximum values 
```{r}

yearly_means <- most_recent_chem%>%
  filter(Campaign %nin% c("CLP  Mainstem-Fort Collins","CLP Mainstem-Canyon" )& site_code %nin% c("BMD","PJW","JWC"  ,"PBR","PBD", "PNF","PSF","SFM","SAWM", "LDRT1", "legacy","timberline","ELC","archery","PFAL") & Year >= 2021)%>%
  select(-c("data_source","Lat","Long","location","Campaign","watershed","status","Buffer_Level","Watershed_Level","distance_upstream_km", "FCW_Number"))%>%
  group_by(Year, site_code, Site)%>%
  summarise(across(starts_with(all_params), mean, na.rm = TRUE),
            .groups = 'drop')

table_data <- yearly_means %>%
  pivot_longer(cols = c(Turbidity:SO4), names_to = "Parameter", values_to = "Value") %>%
  pivot_wider(names_from = Parameter, values_from = Value, names_prefix = paste0(Year, Parameter), values_fill = 0)



subset_table <- yearly_means%>%
  mutate(Site = paste0(Site, " (", site_code, ")"))%>%
  select(Site, Year, Turbidity, TSS, ChlA)%>%
  pivot_longer(cols = c(Turbidity:ChlA), names_to = "Parameter", values_to = "Value")%>%
  pivot_wider(names_from = c(Parameter, Year), values_from = Value, values_fill = 0)%>%
  select(Site, order(colnames(.)))

  

table <- subset_table %>%
  kbl("html", escape = FALSE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, bold = TRUE) %>%
  row_spec(0, bold = TRUE, color = "white", background = "#0073C2") %>%
  collapse_rows(columns = 1:3, valign = "top")%>%
  add_header_above(c(" ", "2021" = 1, "2022" = 1, "2023" = 1, "2021" = 1, "2022" = 1, "2023" = 1, "2021" = 1, "2022" = 1, "2023" = 1  ), bold = TRUE) %>%
  add_header_above(c("Site" = 1, "ChlA" = 3, "TSS" = 3, "Turbidity" = 3))

ft <- flextable(subset_table)%>%
  separate_header() %>%
  align(align = "center", part = "all") %>%
  autofit()

my_theme <- function(x, ...) {
    x <- colformat_double(x, big.mark = "'", decimal.mark = ".", digits = 2)
    x <- set_table_properties(x, layout = "fixed")
    x <- border_remove(x)
    std_border <- fp_border_default(width = 1, color = "black")
    x <- border_outer(x, part="all", border = std_border )
    x <- border_inner_h(x, border = std_border, part="all")
    x <- border_inner_v(x, border = std_border, part="all")
    autofit(x)
}
my_theme(ft)


# Save the table to a Word document
save_as_docx(ft, path = "data/table_export.docx")


```


# Discrete data plots

## Basic Boxplots 
```{r}
source("src/analysis_fxns/build_basic_plot.R")

result_list <- map(all_params, ~build_basic_chem_plot(sites = mainstem_Res_only, param = .x, style = "boxplots"))

walk(result_list, ~print(.))
```

## Basic Timelines
```{r}
source("src/analysis_fxns/build_basic_plot.R")

result_list <- map(all_params, ~build_basic_chem_plot(sites = mainstem_Res_only, param = .x, style = "timeline"))

#Fire affected params
param_oi <- c("SC","K", "NH4" , "NO3","PO4")
param_notitle <- map(param_oi, ~build_basic_chem_plot(sites = mainstem_Res_only, param = .x, style = "timeline",graph_size = 30))


DOC <- build_basic_chem_plot(sites = mainstem_Res_only, param = "DOC", style = "timeline",graph_size = 30, title = TRUE)

param_oi_list <- list(DOC, param_notitle)%>%
  list_flatten()





#Seperate in to burn severity trending params and non trending for SI
ggarrange(plotlist = param_oi_list, ncol = 1)
ggsave("data/figs_output/2023_figs/DRAFT_res_oi_chem.jpg",width = 25, height = 30, dpi = 300)
```


## Reservoir timeline and dotplot
Group 2021+ 2022, summarize to monthly for timeline

```{r}
monthly_res_chla <- filter(most_recent_chem, Year %in% c(2021,2022, 2023) & !is.na(ChlA)& site_code %in% mainstem_Res_only)%>%
  select(site_code, Date, ChlA, Year)%>%
  mutate(month = month(Date, label = TRUE, abbr = TRUE ), 
         year_breakdown = case_when(
           Year %in% c(2021, 2022) ~ "2021 & 2022", 
           Year == 2023 ~ "2023"
         ))%>%
  group_by(site_code,year_breakdown, month)%>%
  summarise(monthly_mean_chla = mean(ChlA))
  
chla_sum_timeline <- ggplot(data = monthly_res_chla, aes(x=month, y=monthly_mean_chla, color=site_code, group=site_code)) +
  geom_line( linewidth=1.5) +
  geom_point( size=5) +
  scale_color_manual(values = colorsBS_site_code)+
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept = 8), color='black', linetype="dashed") +
  labs(x = "Date", y = " Chlorophyll a (μg/L)") +
  theme_bw(base_size=30) +
  theme(legend.position = "none")+
  coord_cartesian(ylim=c(0,12))+
  facet_wrap(~year_breakdown, scales = "free_x")


res_chla <- filter(most_recent_chem, Year %in% c(2021,2022, 2023) & !is.na(ChlA)& site_code %in% mainstem_Res_only)%>%
  select(site_code, Date, ChlA, Year)%>%
  mutate(year_breakdown = case_when(
           Year %in% c(2021, 2022) ~ "2021 & 2022", 
           Year == 2023 ~ "2023"
         ))
res_chla$site_code <- factor(res_chla$site_code, levels = c("LNGR", "JOER", "CBRR", "PTRR", "BRNR"))

chla_sum_dotplot <- ggplot(data = res_chla, aes(x=site_code,y=ChlA, middle=mean(ChlA))) + 
   geom_dotplot(aes(fill=site_code), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .3, dotsize = 1.5)+
  stat_summary(fun = median, geom = "crossbar", position = position_dodge(width = 0.8), width = 0.8, fill = "black") +
  scale_color_manual(values = colorsBS_site_code)+
  scale_fill_manual(values = colorsBS_site_code)+
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept = 8), color='black', linetype="dashed") +
   labs(x = "Site", y = " Chlorophyll a (μg/L)") +
  theme_bw(base_size=30) +
  theme(legend.position = "none",
            strip.background = element_blank(),
            strip.text.x = element_blank())+
  coord_cartesian(ylim=c(0,12))+
  facet_wrap(~year_breakdown, scales = "free_x")


ggarrange(chla_sum_timeline, chla_sum_dotplot, ncol = 1)
ggsave("data/figs_output/2023_figs/DRAFT_res_chla_summary.jpg",width = 20, height = 14, dpi = 300)
```


## Reservoir Dotplots (2021-2023)

Tried to functionalize but the bin size is an issue for other parameters...\
Params that this works for:

-   Chla

-   DOC

-   SO4 (kinda)

-   Ca

-   SC (barely)

```{r}
# graph only res data
source("src/analysis_fxns/build_res_dotplot.R")

chla_dotplot_res <- build_res_dotplot(param = "ChlA")+
#adding meso and eutrophic levels for cold lakes
 geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
    geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
    #annotate(geom="text", label= "MDL Limit (μg/L)", x="CBRR 2022", y=.075, vjust= -1)+
    annotate(geom="text", label= "Mesotrophic", x=1.15, y=2.6, vjust= -1, size = 4)+
    annotate(geom="text", label= "Eutrophic", x= 1.5, y=8, vjust= -1, size = 5)+
   #fixing y axis
    coord_cartesian(ylim=c(0,12))

plot(chla_dotplot_res)
#ggsave("data/figs_output/2023_figs/res_dotplots_2021_2023.jpg", dpi = 300, width = 18, height = 10)

#check out all parameters


test_plots <- map(all_params, build_res_dotplot)

walk(test_plots, ~print(.))
```

## Inflow/Outflow Ratio

Not yet working/ need the full dataset for it to look good in 2023

```{r}


joer_cbrr_ratios <- filter(tidy_chem, site_code %in% c("JOEI",
                                                                "JOER",
                                                                "CBRI",
                                                                "CBRR",
                                                                "CHD"))%>%
      select(Date,site_code,ChlA)%>%
  filter(!is.na(ChlA))%>%
  mutate(site_code = 
           #found typo in dataset, corrected site name from CBRI to CBRR
           case_when((Date == as.Date("2022-10-25")&ChlA == 3.92 ) ~ "CBRR" , 
                               TRUE ~ site_code))%>%
  pivot_wider(id_cols = Date, names_from = site_code, values_from = ChlA)%>%
  mutate(jw_ratio = CBRI / JOEI,
         chambers_ratio = CHD/ CBRI, 
         Year = year(Date))



res_ratio_plot <- filter(joer_cbrr_ratios, Date != "2022-06-14")%>%
  ggplot()+
  geom_line(aes(x=Date, y = jw_ratio, colour ="Joe Wright"), size = 3)+
  geom_line(aes(x=Date, y = chambers_ratio, colour ="Chambers"), size = 3)+
  geom_point(aes(x=Date, y = chambers_ratio, size = CBRR, colour ="Chambers" ))+
  geom_point(aes(x=Date, y = jw_ratio, size = JOER, colour ="Joe Wright"))+
   #geom_text(aes(as.Date("2021-06-15"), 1, label= "Inflow = Outflow", vjust=-1))+
  scale_size_continuous(range = c(2,17))+
  theme_bw(base_size=25) +
  geom_abline(aes(slope=0, intercept=1), color='black', linetype="solid", label = "Inflow = Outflow")+
  labs(size = "Chl-a Levels at Reservoir")+
  scale_color_manual(name = "Reservoir", values = c("Chambers" = "#E69F00", "Joe Wright" = "#56B4E9"))+
 # theme(axis.title.y = element_text(angle = 0, vjust = .5)) +
  labs( x = "Date", y = "Ratio: Outflow Chl-a / Inflow Chl-a" )+
  facet_wrap( ~Year, scales = "free_x" )+
  
  theme(legend.justification = c(.05, .9), legend.position = c(.05, .9),legend.box = "horizontal",
          axis.title = element_text(face = "bold"),
         axis.text.x = element_text(face = "bold"))

#ggsave("output/Res_Ratio.jpg",width = 22, height = 14)
plot(res_ratio_plot)


```

## Longitudinal

Not yet working

```{r}
source("src/paper_figs/build_long_plot.R")


# 2023 weeks "28" "31" "36"
#2022 weeks "22","28","32", "38", "42"

```


## South Fork filled/empty comparison

```{r}
source("src/analysis_fxns/sf_res_impact_plot.R")

sf_plots <- map(.x = all_params, .f = plot_sf_impact)
walk(sf_plots, plot)

sf_chla <- plot_sf_impact(param = "ChlA")+
#adding meso and eutrophic levels for cold lakes
 geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
    geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
    #annotate(geom="text", label= "MDL Limit (μg/L)", x="CBRR 2022", y=.075, vjust= -1)+
    annotate(geom="text", label= "Mesotrophic", x=.75, y=2.6, vjust= -1, size = 6)+
    annotate(geom="text", label= "Eutrophic", x= .75, y=8, vjust= -1, size = 6)
  
ggsave("data/figs_output/2023_figs/sf_impact.jpg", width = 18, height  = 12, dpi = 300)

chla_sf <- sf_impact_df(param = "ChlA")%>%
  filter(location == "Reservoir")
t.test(ChlA ~ filled_status, data = chla_sf)

chla_beav <- sf_impact_df(param = "ChlA")%>%
  filter(site_code == "BEAV")
t.test(ChlA ~ filled_status, data = chla_beav)

```


# Sensor plots

This section works but am waiting on grab sample data from RMRS to make correlation plots between grab sample and lab data
## Time series sensor data
```{r}
source("src/paper_figs/build_ts_plot.R")

# sites <- c("JOEI", "CBRI", "CHD")
# param_oi <- filter(sensor_meta, sensor_meta$key_param == TRUE)%>%
#   pull(param_common)
# 
# combinations <- expand.grid(site_name = c("JOEI", "CBRI", "CHD"), param = param_oi)
# 
# # Use pmap to apply the function to each combination
# plots_list <- pmap(combinations, build_ts_plot)
# 
#       chd_chla <- build_ts_plot(site_name = "chd", param = "chla", color = "#00946c")+
#       theme(axis.title.x = element_blank(), axis.title.y = element_blank())+
#         labs(title = "Chambers Outflow")
#   chd_depth <-build_ts_plot(site_name = "chd",param = "depth",  color = "#0072B2")+
#     theme(axis.title.y = element_blank())
# 
#     cbri_chla <- build_ts_plot(site_name = "cbri", param = "chla", color = "#00946c")+
#      theme(axis.title.x = element_blank())+
#       labs(title = "Joe Wright Outflow/Chambers Inflow")
#     #       axis.title.y = element_blank())
#   cbri_depth <-build_ts_plot(param = "depth", site_name = "cbri", color = "#0072B2")
#   
#   ggarrange(cbri_chla, chd_chla, cbri_depth,chd_depth,  nrow = 2, ncol = 2)
#   #ggsave("test_fig/chla_depth_cbri_chd.jpg", dpi = 300, width = 12, height = 8)
#   
#       joei_chla <- build_ts_plot(site_name = "joei", param = "chla", color = "#00946c")+
#     theme(axis.title.x = element_blank())
#   joei_depth <-build_ts_plot(site_name = "joei",param = "depth",  color = "#0072B2")
#   
#   
#     ggarrange(chd_chla, chd_depth, nrow = 2)
#   #ggsave("test_fig/chla_depth_chd.jpg", dpi = 300)
#   
#   
#   
#    ggarrange(joei_chla, cbri_chla,chd_chla, joei_depth, cbri_depth,chd_depth, nrow = 2, ncol = 3)
#   #ggsave("test_fig/chla_depth_jw_long.jpg", dpi = 300)
#   
#    
#    
#    pbd_turb_grabs <- build_ts_plot(site_name = "pbd", param = "turb", color = "#85722b", start_dt = "2023-07-23 00:00", end_dt = "2023-09-15 00:00", grabs = TRUE)+
#      ylim(0,1000)

 # ggsave("test_fig/turb_pbd_grabs_0809.jpg", dpi = 300, width = 8, height = 6)
```
## Correlate grab and sensor data

```{r}
source("src/analysis_fxns/correlate_grab_sensor.R")

cations_anions <- filter(chem_units, simple %nin% c("Turbidity","TSS","ChlA", "pH", "PO4"))%>%pull(simple)

# Set custom values for sites, sensor_param, timestep, and matched_axes
custom_values <- list(
  sites = "all",
  sensor_param = "actual_cond",
  timestep = "1hour",
  matched_axes = FALSE
)

# Create a partially applied function
partial_correlate_grab_sonde <- partial(correlate_grab_sonde, !!!custom_values)

# Map over the vector
sonde_vs_lab <- map(cations_anions, ~ partial_correlate_grab_sonde(grab_param = .x))

#example function
# correlate_grab_sonde(sites = "all", sensor_param = "spec_cond", grab_param = "Turbidity", timestep = "15min", matched_axes = FALSE)

walk(sonde_vs_lab, ~print(.))

```

