---
title: "Analysis and Figures"
author: "Sam Struthers"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("src/00_analysis_setup.R")
```

# Grab data

```{r}
#discrete sample data and location metadata from most recent pub
DOI = "10372690"
data_version = "v12.13.23b"
source("src/analysis_fxns/grab_zenodo_data.R")

all_params <- chem_units%>%
  pull(simple)
# sensor data
source("src/analysis_fxns/grab_sensor_data.R")

```


## Tidy discrete

```{r}
tidy_chem <- most_recent_chem%>%
  filter(Year > 2020)%>%
  mutate(Date = as.Date(Date, "%m/%d/%y"),
    distance_upstream_km = case_when(site_code == "PFAL" ~ 73.9, TRUE ~ distance_upstream_km), 
         
          dt = case_when(is.na(Time) ~ NA, 
                        TRUE ~ as.POSIXct(paste0(Date, " ", Time), format = "%m/%d/%y %H:%M")))%>%
  left_join(order_table, by = "site_code") 
#site order now added to tidy chem and thus not needed
rm(order_table)

```
## Run above to get data loaded

```{r}
print("Data Successfully loaded for analysis")
```


# Reporting Calculations
These data and calculations will be included in the funder report to give an overview of how the system is changing year to year based on our study

## Chlorophyll a status

In cold water lakes (our study sites), mesotrophic levels are defined as between 2.6 and 8 µg/L, and eutrophic levels are greater than 8 µg/L. Under 2.6 µg/L is considered Oligotrophic. 
```{r}

chla_status_site_year <- tidy_chem%>%
  filter(!is.na(ChlA))%>%
  mutate(eu_status  = case_when(ChlA >= 2.6 &ChlA <= 8 ~ "Mesotrophic", 
                                ChlA > 8 ~ "Eutrophic",
                                ChlA < 2.6 ~ "Oligotrophic"))%>%
  group_by(site_code, Year, eu_status)%>%
  summarise(eu_stats = n())%>%
  ungroup()%>%
  pivot_wider(names_from = eu_status, values_from = eu_stats)%>%
  mutate_at(vars(-Year), ~replace(., is.na(.), 0))%>%
  rowwise()%>%
  mutate(total_samples = sum(c(Eutrophic, Mesotrophic, Oligotrophic)),
    perc_eu = round((Eutrophic/total_samples)*100, digits= 1), 
         perc_meso = round((Mesotrophic/total_samples)*100, digits= 1),
         perc_meso_eu = round(((Eutrophic+Mesotrophic)/total_samples)*100, digits= 1), 
        perc_oligo = round((Oligotrophic/total_samples) *100, digits= 1),
    Year = as.character(Year))


long_chla_status <- chla_status_site_year%>%
  select(site_code, Year, total_samples, perc_eu, perc_meso, perc_meso_eu, perc_oligo)%>%
  pivot_longer(cols = c(perc_eu, perc_meso, perc_meso_eu, perc_oligo), names_to = "category", values_to = "value" )

status_plot <- long_chla_status%>%
  filter(site_code %in% mainstem_Res_only )%>%
  ggplot(aes(x = Year, y = value,group = site_code, color =  site_code))+
  scale_color_manual(values = colorsBS_site_code)+
 geom_line()+
   geom_point()+
  theme_bw(base_size = 15)+
facet_wrap(~category)
plot(status_plot)



```

## chla stats

```{r}


chla_per_year <-tidy_chem%>%
  select(ChlA, Year, site_code, Date, watershed)%>%
  na.omit()%>%
  group_by(Year)%>%
  summarise(count_year = n())


chla_per_site_year <-tidy_chem%>%
  select(ChlA, Year, site_code)%>%
  na.omit()%>%
  group_by(Year, site_code)%>%
  summarise(n = n(), 
         mean = mean(ChlA), 
         median = median(ChlA))%>%
  ungroup()%>%
  dplyr::arrange(site_code,Year)

```

# Mean all params

Code to make SI tables for minimum and maximum values 
```{r}

yearly_means <- tidy_chem%>%
  filter(Campaign %nin% c("CLP  Mainstem-Fort Collins","CLP Mainstem-Canyon" )& site_code %nin% c("PJW","JWC"  ,"PBR","PBD", "PNF","PSF","SFM","SAWM", "LDRT1", "legacy","timberline","ELC","archery","PFAL", "BEAV") & Year >= 2021)%>%
  select(-c("data_source","Lat","Long","location","Campaign","watershed","status","Buffer_Level","Watershed_Level","distance_upstream_km", "FCW_Number", "Field_DO_mgL","Field_Cond_µS/cm","Field_Temp_C"))%>%
  group_by(Year, site_code, Site)%>%
  summarise(across(starts_with(all_params), mean, na.rm = TRUE),
            .groups = 'drop')
 


  
  subset_table <- yearly_means%>%
  mutate(Site = paste0(Site, " (", site_code, ")"))%>%
    #select(Site, Year, `Chlorophyll a (ug/L)` = ChlA,     `SC (uS/cm)` = SC,    pH,    `DOC (mg/L)` = DOC)%>%
  #select(Site, Year,`TDN (mg/L)` = DTN,     `NH4 (mg/L)` = NH4,   	`NO3 (mg/L)` = NO3,   `PO4 (mg/L)` = PO4 )%>%
  #select(Site, Year,`SO4 (mg/L)` = SO4,     `Na (mg/L)` = Na,   	`Ca (mg/L)` = Ca,   `Cl (mg/L)` = Cl )%>%
  select(Site, Year,`K (mg/L)` = K,     `Mg (mg/L)` = Mg,   	`F (mg/L)` = `F`, TSS)%>%
    
  pivot_longer(cols = 
                   #c(`Chlorophyll a (ug/L)`:`DOC (mg/L)`),
                  #c(`TDN (mg/L)`:`PO4 (mg/L)`),
               #c(`SO4 (mg/L)`:`Cl (mg/L)`),
               c(`K (mg/L)`:TSS),
               names_to = "Parameter", values_to = "Value")%>%
  pivot_wider(names_from = c(Parameter, Year), values_from = Value, values_fill = 0)%>%
  select(Site, order(colnames(.)))

  subset_table$Site <- factor(subset_table$Site, levels = c("Barnes Meadow Outflow (BMD)", "Barnes Meadow Reservoir (BRNR)", "Chambers Inlet (CBRI)", "Chambers Reservoir (CBRR)", "Chambers Outflow (CHD)", "Joe Wright Inlet (JOEI)", "Joe Wright Reservoir (JOER)", "Comanche Inflow (COMI)",  "Comanche Reservoir (COMR)", "Comanche Outflow (COMO)", "Hourglass Inflow (HORI)", "Hourglass Reservoir (HORR)", "Hourglass Outflow (HORO)","Long Draw Outlet (LNGO)","Long Draw Reservoir (LNGR)","Peterson Outlet (PTRO)", "Peterson Reservoir (PTRR)"     ))

  #create standard border color and width
  std_border <- fp_border_default(width = 1, color = "black")
  
ft <- flextable(subset_table)%>%
  separate_header() %>%
  align(align = "center", part = "all")%>%
  colformat_double( big.mark = "'", decimal.mark = ".", digits = 2)%>%
  set_table_properties(layout = "fixed")%>%
  border_remove()%>%
  border_outer(part="all", border = std_border )%>%
  border_inner_h(border = std_border, part="all")%>%
   border_inner_v(border = std_border, part="all")%>%
  autofit()%>%
  italic( j = "Site")%>%
  fontsize( size = 8, part = "body")

#Highlighting columns other than Site
# Max is red
# min is blue
columns_to_highlight <- names(subset_table) %>%
  keep(~ !grepl("Site", .))

  for (i in 1:length(columns_to_highlight)) {
    max_color <- "#CC3311"
    min_color <- "#0077BB"
    
    ft <- color(ft, j = i+1, 
                    i = ~ subset_table[i+1] == max(subset_table[i+1], na.rm = TRUE), 
                    color = max_color)
    
    ft <- color(ft, j = i+1, 
                    i = ~ subset_table[i+1] == min(subset_table[i+1], na.rm = TRUE), 
                    color = min_color)
  }
  

ft

  
sect_properties <- prop_section(
  page_size = page_size(
    orient = "landscape",
    width = 8.3, height = 11.7
  ),
  type = "continuous",
  page_margins = page_mar()
)

ft

# Save the table to a Word document
save_as_docx(ft, path = "data/table_export3.docx", pr_section = sect_properties)



```



# Discrete data plots

## Basic Boxplots 
```{r}
source("src/analysis_fxns/build_basic_plot.R")

all_res_sites <- c("LNGR", "JOER","COMR", "HORR",  "CBRR", "PTRR", "BRNR")


#Plot 1
title_1 <- "ChlA"
title_1 <- build_basic_chem_plot(sites = all_res_sites, style = "boxplot", graph_size = 25, param = title_1, title = TRUE)
param_oi_1 <- c("DOC", "DTN", "pH", "K","NH4","NO3","PO4")
param_notitle1 <- map(param_oi_1, ~build_basic_chem_plot(sites = all_res_sites, param = .x, style = "boxplot", graph_size = 25))
list1 <- list(title_1, param_notitle1)%>%
  list_flatten()

ggarrange(plotlist = list1, ncol = 1)
ggsave(filename = "data/figs_output/2023_figs/res_chem_boxplots1.jpg",width = 24, height = 30, dpi = 300)




#Plot 2
title_2 <- "ANC"
title_2 <- build_basic_chem_plot(sites = all_res_sites, style = "boxplot", graph_size = 25, param = title_2, title = TRUE)
param_oi_2 <- c("SC" ,"Na", "Mg","Ca", "F","Cl","SO4")
param_notitle2 <- map(param_oi_2, ~build_basic_chem_plot(sites = all_res_sites, param = .x, style = "boxplot", graph_size = 25))
list2 <- list(title_2, param_notitle2)%>%
  list_flatten()

ggarrange(plotlist = list2, ncol = 1)
ggsave(filename = "data/figs_output/2023_figs/res_chem_boxplots2.jpg",width = 24, height = 30, dpi = 300)
```

## Basic Timelines
```{r}
source("src/analysis_fxns/build_basic_plot.R")

result_list <- map(all_params, ~build_basic_chem_plot(sites = mainstem_Res_only, param = .x, style = "timeline"))

#Fire affected params
param_oi <- c("SC","K", "NH4" , "NO3","PO4")
param_notitle <- map(param_oi, ~build_basic_chem_plot(sites = mainstem_Res_only, param = .x, style = "timeline",graph_size = 30))


DOC <- build_basic_chem_plot(sites = mainstem_Res_only, param = "DOC", style = "timeline",graph_size = 30, title = TRUE)

param_oi_list <- list(DOC, param_notitle)%>%
  list_flatten()





#Seperate in to burn severity trending params and non trending for SI
ggarrange(plotlist = param_oi_list, ncol = 1)
ggsave("data/figs_output/2023_figs/DRAFT_res_oi_chem.jpg",width = 25, height = 30, dpi = 300)
```


## Reservoir timeline and dotplot
Group 2021+ 2022, summarize to monthly for timeline

```{r}
monthly_res_chla <- filter(tidy_chem, Year %in% c(2021,2022, 2023) & !is.na(ChlA)& site_code %in% mainstem_Res_only)%>%
  select(site_code, Date, ChlA, Year)%>%
  mutate(month = month(Date, label = TRUE, abbr = TRUE ), 
         year_breakdown = case_when(
           Year %in% c(2021, 2022) ~ "2021 & 2022", 
           Year == 2023 ~ "2023"
         ))%>%
  group_by(site_code,year_breakdown, month)%>%
  summarise(monthly_mean_chla = mean(ChlA))
  

res_chla <- filter(tidy_chem, Year %in% c(2021,2022, 2023) & !is.na(ChlA)& site_code %in% mainstem_Res_only)%>%
  select(site_code, Date, ChlA, Year)%>%
mutate(Date = as.Date(Date, format("%m/%d/%y")))

chla_sum_timeline <- ggplot(data = res_chla, aes(x=Date, y=ChlA, color=site_code, group=site_code)) +
  geom_line( linewidth=1.5) +
  geom_point( size=5) +
  scale_color_manual(values = colorsBS_site_code)+
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept = 8), color='black', linetype="dashed") +
  labs(x = "Date", y = " Chlorophyll a (μg/L)") +
  theme_bw(base_size=30) +
  theme(legend.position = "none")+
  coord_cartesian(ylim=c(0,12))+
  scale_x_date(date_breaks = "months", date_labels = "%b")+
  facet_wrap(~Year, scales = "free_x")


res_chla <- filter(tidy_chem, Year %in% c(2021,2022, 2023) & !is.na(ChlA)& site_code %in% mainstem_Res_only)%>%
  select(site_code, Date, ChlA, Year)%>%
  mutate(year_breakdown = case_when(
           Year %in% c(2021, 2022) ~ "2021 & 2022", 
           Year == 2023 ~ "2023"
         ))
res_chla$site_code <- factor(res_chla$site_code, levels = c("LNGR", "JOER", "CBRR", "PTRR", "BRNR"))

chla_sum_dotplot <- ggplot(data = res_chla, aes(x=site_code,y=ChlA, middle=mean(ChlA))) + 
   geom_dotplot(aes(fill=site_code), stackgroups = FALSE, binaxis = "y", method = "histodot",stackdir = "center", position = "dodge", binwidth = .3, dotsize = 1.5)+
  stat_summary(fun = median, geom = "crossbar", position = position_dodge(width = 0.8), width = 0.8, fill = "black") +
  scale_color_manual(values = colorsBS_site_code)+
  scale_fill_manual(values = colorsBS_site_code)+
  geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
  geom_abline(aes(slope=0, intercept = 8), color='black', linetype="dashed") +
   labs(x = "Site", y = " Chlorophyll a (μg/L)") +
  theme_bw(base_size=30) +
  theme(legend.position = "none",
            strip.background = element_blank(),
            strip.text.x = element_blank())+
  coord_cartesian(ylim=c(0,12))+
  facet_wrap(~Year, scales = "free_x")


ggarrange(chla_sum_timeline, chla_sum_dotplot, ncol = 1)
ggsave("data/figs_output/2023_figs/res_chla_dotplot_timeline.jpg",width = 24, height = 14, dpi = 300)
```


## Reservoir Dotplots (2021-2023)

Tried to functionalize but the bin size is an issue for other parameters...\
Params that this works for:

-   Chla

-   DOC

-   SO4 (kinda)

-   Ca

-   SC (barely)

```{r}
# graph only res data
source("src/analysis_fxns/build_res_dotplot.R")

chla_dotplot_res <- build_res_dotplot(param = "ChlA")+
#adding meso and eutrophic levels for cold lakes
 geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
    geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
    #annotate(geom="text", label= "MDL Limit (μg/L)", x="CBRR 2022", y=.075, vjust= -1)+
    annotate(geom="text", label= "Mesotrophic", x=1.15, y=2.6, vjust= -1, size = 4)+
    annotate(geom="text", label= "Eutrophic", x= 1.5, y=8, vjust= -1, size = 5)+
   #fixing y axis
    coord_cartesian(ylim=c(0,12))

plot(chla_dotplot_res)
ggsave("data/figs_output/2023_figs/res_dotplots_2021_2023.jpg", dpi = 300, width = 18, height = 10)

#check out all parameters


test_plots <- map(all_params, build_res_dotplot)

walk(test_plots, ~print(.))
```

## Inflow/Outflow Ratio

Not yet working/ need the full dataset for it to look good in 2023

```{r}


joer_cbrr_ratios <- filter(tidy_chem, site_code %in% c("JOEI",
                                                                "JOER",
                                                                "CBRI",
                                                                "CBRR",
                                                                "CHD"))%>%
      select(Date,site_code,ChlA)%>%
  filter(!is.na(ChlA))%>%
  mutate(site_code = 
           #found typo in dataset, corrected site name from CBRI to CBRR
           case_when((Date == as.Date("2022-10-25")&ChlA == 3.92 ) ~ "CBRR" , 
                               TRUE ~ site_code))%>%
  pivot_wider(id_cols = Date, names_from = site_code, values_from = ChlA)%>%
  mutate(jw_ratio = CBRI / JOEI,
         chambers_ratio = CHD/ CBRI, 
         Year = year(Date))



res_ratio_plot <- filter(joer_cbrr_ratios, Date != "2022-06-14")%>%
  ggplot()+
  geom_line(aes(x=Date, y = jw_ratio, colour ="Joe Wright"), size = 3)+
  geom_line(aes(x=Date, y = chambers_ratio, colour ="Chambers"), size = 3)+
  geom_point(aes(x=Date, y = chambers_ratio, size = CBRR, colour ="Chambers" ))+
  geom_point(aes(x=Date, y = jw_ratio, size = JOER, colour ="Joe Wright"))+
   #geom_text(aes(as.Date("2021-06-15"), 1, label= "Inflow = Outflow", vjust=-1))+
  scale_size_continuous(range = c(2,17))+
  theme_bw(base_size=25) +
  geom_abline(aes(slope=0, intercept=1), color='black', linetype="solid", label = "Inflow = Outflow")+
  labs(size = "Chl-a Levels at Reservoir")+
  scale_color_manual(name = "Reservoir", values = c("Chambers" = "#E69F00", "Joe Wright" = "#56B4E9"))+
 # theme(axis.title.y = element_text(angle = 0, vjust = .5)) +
  labs( x = "Date", y = "Ratio: Outflow Chl-a / Inflow Chl-a" )+
  facet_wrap( ~Year, scales = "free_x" )+
  
  theme(legend.justification = c(.05, .9), legend.position = c(.05, .9),legend.box = "horizontal",
          axis.title = element_text(face = "bold"),
         axis.text.x = element_text(face = "bold"))

#ggsave("output/Res_Ratio.jpg",width = 22, height = 14)
plot(res_ratio_plot)


```

## Longitudinal

Not yet working

```{r}
source("src/analysis_fxns/build_long_plot.R")

#Stuff for testing

choosen_dates_chambers <- as.Date(c(#"2022-06-01",
  "2022-06-14",
  #"2022-07-05",
  "2022-07-26",
  "2022-08-16",
  #"2022-08-23",  
  #"2022-08-30",
  #"2022-09-06",
  #"2022-09-13",
  # "2022-09-20",
  "2022-09-27",
  #"2022-10-04",
  #"2022-10-11",
  "2022-10-18"
  #"2022-10-25",
  #"2022-11-01"
))

chambers_dates_2023 <- c("2023-06-09","2023-06-15", 
                         "2023-09-05", 
                         #"2023-09-21", 
                         "2023-10-05", 
                         #"2023-10-10", 
                         "2023-10-16")


    #chambers dataframe
    chambers_longitudinal <- tidy_chem %>%
      dplyr::filter(!is.na(ChlA)) %>%
      dplyr::filter(site_code %in% c("JOEI", "JOER", "CBRR", "CBRI", "CHD")) %>%
      dplyr::filter(Date %in% chambers_dates_2023)%>%
      mutate(Date=as.character(Date),
             location_type = ifelse(location == "Outflow"|location =="Inflow", "Stream", "Reservoir"))
    
    ###PLOTING PART OF FUNCTION
    
    #chla graph
    chambers_chla_long <- chambers_longitudinal%>%
      ggplot(aes(x=Distance, y=ChlA, color=Date)) +
      geom_point( aes(shape = location_type), size=8, alpha = .7) +
      geom_line(aes(x=Xdistance), size=2, alpha = .7) +
      geom_point(aes(shape = location_type), size=8, alpha = .7) +
      scale_color_manual(values = season_color_vals)+
      scale_fill_manual(values = season_color_vals)+
      theme_bw(base_size=30) +
      labs(shape = "", color="") +
      theme(axis.text.x = element_blank(), 
            legend.text = element_text(size = 18)) +
      xlab("") +
      ylab("Chlorophyll a (μg/L)")
    
    #NO3 GRAPH
    chambers_no3_long <- chambers_longitudinal%>%
      ggplot(aes(x=Distance, y=NO3, color=Date)) +
      geom_point( aes(shape = location_type), size=8, alpha = .7) +
      geom_line(aes(x=Xdistance), size=2, alpha = .7) +
      geom_point(aes(shape = location_type), size=8, alpha = .7) +
      scale_color_manual(values = season_color_vals)+
      scale_fill_manual(values = season_color_vals) +
      theme_bw(base_size=30) +
      theme(legend.text = element_text(size =18))+
      labs(shape = "", color="") +
      scale_x_discrete(labels=c("1 - JOEI" = "Above Joe Wright", "2 - JOER" = "", "3 - CBRI" = "Above Chambers",
                                "4 - CBRR" = "", "5 - CHD" = "Below Chambers")) +
      xlab("Longitudinal Profile") +
      ylab("NO3 (mg/L)")
    
    
    chambers_plot <- ggarrange(chambers_chla_long,chambers_no3_long, ncol=1, nrow=2, common.legend=T)
    
    chambers_plot

ggsave("data/figs_output/2023_figs/jwc_long_2023.jpg", width = 15, height  = 10, dpi = 300)

# 2023 weeks "28" "31" "36"
#2022 weeks "22","28","32", "38", "42"

```

## CLP Longitudinal

```{r}


    
    date_df <- tibble( date_col = as.Date(dates), 
                         wk =  as.character(week(date_col)),
                        year =as.character(year(date_col)),
                           wk_year = paste(year, wk), 
                       date_char = as.character(dates))
    
    
    weeks_select2022 <- filter(date_df, year == 2022)%>%
      pull(wk)
    weeks_select2023 <- filter(date_df, year == 2023)%>%
      pull(wk)
    week_all <- date_df%>% pull(wk)
    
    
    longitudinal_res_mainstem <- filter(tidy_chem, Year %in% c(2022, 2023)& Date != "2022-09-19")%>%
      filter ( site_code %in% c("JOEI","JOER","CBRI","CBRR","CHD", "JWC", "SLEP", "PFAL",
                                "PBR","PSF","PNF","PBD") & !is.na(ChlA))%>%
      select(site_code,Date, distance_upstream_km, ChlA, NO3, PO4, K, status, location, watershed )%>%
      mutate(wk = as.character(week(Date)))
    # %>%
    #   filter(wk %in% weeks_select2022 )
    
    longitudinal_res_mainstem_both <- filter(tidy_chem, Year == "2023")%>%
      filter ( site_code %in% c("JOEI","JOER","CBRI","CBRR","CHD", "JWC", "SLEP", "PFAL",
                                "PBR","PSF","PNF","PBD"))%>%
      select(site_code,Date, watershed, distance_upstream_km, ChlA, NO3, PO4, K, status, location )%>%
      mutate(wk = as.character(week(Date)))%>%
      #filter(wk %in% weeks_select2023 )%>%
        rbind(longitudinal_res_mainstem_2022)%>%
        mutate(dist_pbd = as.character(distance_upstream_km),
               site_code  = case_when(site_code == "PFAL" ~ "SLEP", TRUE ~ site_code),
               type = ifelse(location %in% c("Inflow","Outflow"),"Stream",
                             ifelse(location == "Reservoir", "Reservoir", "Mainstem")))
      
      
    
    
    longitudinal_res_mainstem$wk <- factor(longitudinal_res_mainstem$wk, levels = week_all)
    longitudinal_res_mainstem$type <- factor(longitudinal_res_mainstem$type, levels = c("Stream", "Reservoir", "Mainstem"))
    
    
    long_clp_monthly <- filter(tidy_chem, !is.na(ChlA)& Year > 2021)%>%
      filter ( site_code %in% c("JOEI","JOER","CBRI","CBRR","CHD", "JWC", "SLEP", "PFAL",
                                "PBR","PSF","PNF","PBD"))%>%
      select(site_code,Date, watershed, distance_upstream_km, ChlA, NO3, status, location, Year )%>%
      mutate(month = month(Date,label= TRUE,  abbr = TRUE),
             month_num = month(Date), 
             dist_pbd = distance_upstream_km,
             site_code  = case_when(site_code == "PFAL" ~ "SLEP", TRUE ~ site_code),
             type = ifelse(location %in% c("Inflow","Outflow"),"Stream",
                             ifelse(location == "Reservoir", "Reservoir", "Mainstem")))%>%
      filter(month_num > 5 & month_num < 11)%>%
      group_by(Year, month, site_code, type, dist_pbd)%>%
      summarise(chla_median = median(ChlA, na.rm = TRUE), 
                n_samples = n())
    
    
    
    #graphing
    
    long_clp_graph_monthly <- long_clp_monthly%>%
      ggplot()+
      geom_point(aes(x = dist_pbd, y= chla_median, shape = type, color = month), alpha = .9, size = 8)+
      geom_line(aes(x = dist_pbd, y= chla_median, group = month, color =  month), size = 4, alpha = .8)+
      geom_point(aes(x = dist_pbd, y= chla_median, shape = type, color = month), alpha = .9, size = 8)+
      #gghighlight(wk == "30", use_direct_label = FALSE )+
      theme_bw(base_size = 20)+
      scale_x_reverse()+
      scale_color_manual(name = "Month: ", values = c("Jun" = "#047E82", "Jul" = "#397534",  "Aug"= '#59B851', "Sep" = '#DEB907', "Oct" = '#FA850E' ))+
      scale_shape_manual(values=c(17, 16, 15))+
       scale_fill_manual( values = c("Jun" = "#047E82", "Jul" = "#397534",  "Aug"= '#59B851', "Sep" = '#DEB907', "Oct" = '#FA850E'  ))+
      # # scale_color_manual(name = "Week of", values = c("6-01" = "#047E82", "7-11" = "#397534", "7-25"='#59B851', "8-08"= '#DEB907' ))+
      labs(shape = "Site Type", color="", fill ="") +
      theme(legend.justification = c(.9,.9) , legend.position = c(.9, .9),
            #legend.box.background  = element_rect(color = "black",size = 1.5),
            axis.title = element_text(face = "bold"),
            axis.text.x = element_text(face = "bold"))+
      #theme(axis.text.x = element_blank()) +
      xlab("Distance from Canyon Mouth (km)") +
      ylab("Chlorophyll a (μg/L)")+
      facet_wrap(~Year, nrow = 2)
    
   long_clp_graph_monthly
    ggsave("data/figs_output/2023_figs/long_clp_monthly.jpg", width = 20, height = 15, dpi = 300)

```



## South Fork filled/empty comparison

```{r}
source("src/analysis_fxns/sf_res_impact_plot.R")

# sf_plots <- map(.x = all_params, .f = plot_sf_impact)
# walk(sf_plots, plot)

sf_chla <- plot_sf_impact(param = "ChlA")+
#adding meso and eutrophic levels for cold lakes
 geom_abline(aes(slope=0, intercept=2.6), color='black', linetype="dashed") +
    geom_abline(aes(slope=0, intercept=8), color='black', linetype="dashed") +
    #annotate(geom="text", label= "MDL Limit (μg/L)", x="CBRR 2022", y=.075, vjust= -1)+
    annotate(geom="text", label= "Mesotrophic", x=.75, y=2.6, vjust= -1, size = 6)+
    annotate(geom="text", label= "Eutrophic", x= .75, y=8, vjust= -1, size = 6)

sf_no3 <- plot_sf_impact(param = "NO3")
sf_no3
sf_k <- plot_sf_impact(param = "K")
sf_k
  
  

ggsave("data/figs_output/2023_figs/sf_impact.jpg", width = 18, height  = 12, dpi = 300)



sf_DTN<- plot_sf_impact(param = "DTN")
sf_DTN


no3_sf <- sf_impact_df(param = "NO3")%>%
  filter(location %in% c("Reservoir"))
t.test(NO3 ~ filled_status, data = no3_sf)

chla_sf <- sf_impact_df(param = "ChlA")%>%
  filter(site_code == "SFM")
t.test(ChlA ~ filled_status, data = chla_sf)

chla_beav <- sf_impact_df(param = "ChlA")%>%
  filter(site_code == "BEAV")
t.test(ChlA ~ filled_status, data = chla_beav)

```


# Sensor plots

This section works but am waiting on grab sample data from RMRS to make correlation plots between grab sample and lab data
## Time series sensor data
```{r}
source("src/analysis_fxns/build_ts_plot.R")

# sites <- c("JOEI", "CBRI", "CHD")
# param_oi <- filter(sensor_meta, sensor_meta$key_param == TRUE)%>%
#   pull(param_common)
# 
# combinations <- expand.grid(site_name = c("JOEI", "CBRI", "CHD"), param = param_oi)
# 
# # Use pmap to apply the function to each combination
# plots_list <- pmap(combinations, build_ts_plot)

      chd_chla <- build_ts_plot(site_name = "chd", param = "chla", color = "#00946c", grabs = TRUE)+
       theme(axis.title.x = element_blank())+
         labs(title = "Site: Chambers Outflow (CHD)")
   chd_depth <-build_ts_plot(site_name = "chd",param = "depth",  color = "#0072B2", grabs = TRUE)
   ggarrange(chd_chla,chd_depth,  nrow = 2, ncol = 1)
   ggsave(filename = "data/figs_output/2023_figs/chla_depth_chd.jpg", width = 12, height = 10,  dpi = 300)
   
#     cbri_chla <- build_ts_plot(site_name = "cbri", param = "chla", color = "#00946c")+
#      theme(axis.title.x = element_blank())+
#       labs(title = "Joe Wright Outflow/Chambers Inflow")
#     #       axis.title.y = element_blank())
#   cbri_depth <-build_ts_plot(param = "depth", site_name = "cbri", color = "#0072B2")
#   
#   ggarrange(cbri_chla, chd_chla, cbri_depth,chd_depth,  nrow = 2, ncol = 2)
#   #ggsave("test_fig/chla_depth_cbri_chd.jpg", dpi = 300, width = 12, height = 8)
#   
#       joei_chla <- build_ts_plot(site_name = "joei", param = "chla", color = "#00946c")+
#     theme(axis.title.x = element_blank())
#   joei_depth <-build_ts_plot(site_name = "joei",param = "depth",  color = "#0072B2")
#   
#   
#     ggarrange(chd_chla, chd_depth, nrow = 2)
#   #ggsave("test_fig/chla_depth_chd.jpg", dpi = 300)
#   
#   
#   
#    ggarrange(joei_chla, cbri_chla,chd_chla, joei_depth, cbri_depth,chd_depth, nrow = 2, ncol = 3)
#   #ggsave("test_fig/chla_depth_jw_long.jpg", dpi = 300)
#   
#    
#    
#    pbd_turb_grabs <- build_ts_plot(site_name = "pbd", param = "turb", color = "#85722b", start_dt = "2023-07-23 00:00", end_dt = "2023-09-15 00:00", grabs = TRUE)+
#      ylim(0,1000)

 # ggsave("test_fig/turb_pbd_grabs_0809.jpg", dpi = 300, width = 8, height = 6)
```
## Correlate grab and sensor data

```{r}
source("src/analysis_fxns/correlate_grab_sensor.R")

cations_anions <- filter(chem_units, simple %nin% c("Turbidity","TSS","ChlA", "pH", "PO4"))%>%pull(simple)

# Set custom values for sites, sensor_param, timestep, and matched_axes
custom_values <- list(
  sites = "all",
  sensor_param = "actual_cond",
  timestep = "1hour",
  matched_axes = FALSE
)

sites_select <- c("CBRI", "PBD", "JOEI", "SFM")

correlate_grab_sonde(sites = "all" , sensor_param = "FDOM", grab_param = "DOC", timestep = "1hour", matched_axes = FALSE)

# Create a partially applied function
partial_correlate_grab_sonde <- partial(correlate_grab_sonde, !!!custom_values)

# Map over the vector
sonde_vs_lab <- map(cations_anions, ~ partial_correlate_grab_sonde(grab_param = .x))

#example function
# correlate_grab_sonde(sites = "all", sensor_param = "spec_cond", grab_param = "Turbidity", timestep = "15min", matched_axes = FALSE)

walk(sonde_vs_lab, ~print(.))

```

