---
title: "Temp Figures and Trends for CPL lakes"
author: "B Steele"
format: html
editor: visual
---

## Purpose

Create some compelling figures from the Landsat-derived surface temperature dataset.

## Prep environment

```{r}
library(tidyverse)
library(ggthemes)
library(anomalize)
library(ggplot2)
library(cowplot)
knitr::opts_knit$set(root.dir = "~/Repositories/cameron_peak_fire_study/CPL")
```

## Prep data

Filter out the anomalous data

```{r}
tempData <- read_csv("CPL/data/CLP_flagged_SurfTemp_Landsat5-9_v02Dec2022.csv")%>% 
  filter(anomaly == 'No') %>% 
  mutate(date = as.Date(date, format = "%m/%d/%Y"))

```

Do a quick vis:

```{r}
ggplot(tempData, aes(x = date, y = SurfTemp_degC, color = Name)) +
  geom_point() +
  facet_grid(Name ~ .) +
  theme_bw() +
  scale_color_colorblind()
```

For consistency, let's just look at data after L7 came online (April 1999)

```{r}
tempData_recent <- tempData %>% 
  filter(date >= as.Date('1999-04-01'))

ggplot(tempData_recent, aes(x = date, y = SurfTemp_degC, color = Name)) +
  geom_point() +
  facet_grid(Name ~ .) +
  theme_bw() +
  scale_color_colorblind()
```

## Time Series Analysis

Let's use the `anomalize` package to determine the season-adjusted trends for each lake using functions.

```{r}
formatData = function(lake){
  lakeData <- tempData_recent %>% 
    filter(Name == lake)
  as_tibble(lakeData)
}


calcSeasonAdjTrends = function(lakeTibble){
  lakeTibble %>% 
    time_decompose(SurfTemp_degC, merge = T) 
}

graphTrendObs = function(seasonAdjTrends) {
  lakeName = seasonAdjTrends$Name[1]
  ggplot(seasonAdjTrends, aes(x = date, y = observed)) +
    geom_point(color = 'gray') +
    labs(x = NULL, 
         y = NULL,
         title = paste0(lakeName)) +
    geom_point(aes(y = trend), color = '#E69F00') +
    geom_smooth(aes(y = trend), lty = 2) +
    theme_bw() +
    theme(plot.title = element_text(face = 'bold', hjust = 0.5, size = 12))
}
```

Apply functions to each reservoir

```{r}

BM = formatData('Barnes Meadow Reservoir')
BM_trends = calcSeasonAdjTrends(BM)
BMRes = graphTrendObs(BM_trends)

CL = formatData('Chambers Lake')
CL_trends = calcSeasonAdjTrends(CL)
CLake = graphTrendObs(CL_trends)

HaR = formatData('Halligan Reservoir')
HaR_trends = calcSeasonAdjTrends(HaR)
HalliganRes <- graphTrendObs(HaR_trends)

HoR = formatData('Horsetooth Reservoir')
HoR_trends = calcSeasonAdjTrends(HoR)
HorsetoothRes <- graphTrendObs(HoR_trends)

JW = formatData('Joe Wright Reservoir')
JW_trends = calcSeasonAdjTrends(JW)
JWRes <- graphTrendObs(JW_trends)

LD = formatData('Long Draw Reservoir')
LD_trends = calcSeasonAdjTrends(LD)
LDRes <- graphTrendObs(LD_trends)

MS = formatData('Milton Seaman Reservoir')
MS_trends = calcSeasonAdjTrends(MS)
MSRes <- graphTrendObs(MS_trends)

PL = formatData('Peterson Lake')
PL_trends = calcSeasonAdjTrends(PL)
PLake <- graphTrendObs(PL_trends)

```

Plot them together

```{r}
plot_grid(NULL, BMRes, 
          NULL, CLake, 
          NULL, HalliganRes, 
          NULL, HorsetoothRes, 
          NULL, JWRes, 
          NULL, LDRes, 
          NULL, MSRes, 
          NULL, PLake, 
          ncol = 2, 
          rel_widths = c(0.05, 0.95))+
draw_label("estimated lake surface temperature (°C)", x=  0, y=0.5, vjust= 1.5, angle=90)

ggsave('stacked_temptrends_CLP.jpg',
       height = 9, 
       width = 12,
       dpi = 300)
```

## Put them back together

Rejoin all

```{r}
tempTrends <- full_join(Barnes, Chambers) %>% 
  full_join(., Halligan) %>% 
  full_join(., Horsetooth) %>% 
  full_join(., JoeWright) %>% 
  full_join(., LongDraw) %>% 
  full_join(., MiltonSeaman) %>% 
  full_join(., Peterson)
```

And let's select just lake, date, temp, and the trend and then orient vertically to plot

```{r}
tempTrends_vert <- tempTrends %>% 
  select(Name, date, SurfTemp_degC, trend) %>% 
  pivot_longer(names_to = 'temp_var', values_to = 'value', cols = c(SurfTemp_degC, trend))
```

And now plot together

```{r}
ggplot(tempTrends_vert, aes(x = date, y = value, color = temp_var)) +
  geom_point() +
  facet_grid(Name ~ .) +
  labs(x = NULL, y = 'Landsat-derived surface temperature (degC)') +
  theme_bw() + 
  scale_color_colorblind() +
  theme(legend.position = 'bottom')
```
